---
title: "Teotihuacan AMM, Script #2:"
subtitle: "Analysis"
author: "Rudolf Cesaretti"
date: "Last run on `r Sys.Date()`"
output:
  html_document:
    toc: true
    df_print: paged
    number_sections: true
---


```{r, setup, include=FALSE,echo=FALSE, message=FALSE,warning=FALSE}
require(knitr)
# Set so that long lines in R will be wrapped:
opts_chunk$set(tidy.opts=list(width.cutoff=75),tidy=TRUE)
#
rm(list = ls())
```


  
# Setup 

All of the data and scripts are downloadable from the [new Teotihuacan AMM Analysis github repository](https://https://github.com/rcesaret/TeotihuacanAMM), which can be cloned to your own account/computer or downloaded directly as a .zip folder.

Either way, once you have done so, you will need to modify the working directory (setwd("C:/...)") path and "dir" variables in the code chunk below to match the repository location on your computer.

```{r, label='Set Local Directory Location', message=FALSE, warning=FALSE}

wd <- list()

#SET YOUR LOCAL DIRECTORY LOCATION HERE:
#wd$dir <- "C:/Users/rcesaret/Dropbox (ASU)/TeotihuacanDean/TeotihuacanAMM/"
wd$dir <- "C:/Users/TJ McMote/Dropbox (ASU)/TeotihuacanDean/TeotihuacanAMM/"

wd$analysis <- paste0(wd$dir,"analysis/")
wd$data_r <- paste0(wd$dir,"data-raw/")
wd$data_p <- paste0(wd$dir,"data-processed/")
wd$data_f <- paste0(wd$dir,"data-final-outputs/")
wd$figs <- paste0(wd$dir,"figures/")
wd$funcs <- paste0(wd$dir,"functions/")

```



## Load R Packages and Custom Functions




```{r, label='Load Libraries', message=FALSE,warning=FALSE}
# Package names
packages <- c("rgdal", "rgeos", "sp", "sf", "GISTools", "raster","stars", "spatstat",
              "tidyverse", "tidyr", "nls.multstart", "nlme", "brms", "broom", 
              "ggrepel", "minpack.lm", "data.table", "zoo", "lmtest", "sandwich", 
              "nlstools", "MASS", "NSM3", "gridExtra", "ggnewscale", "cowplot", 
              "scales", "viridis", "Cairo")

# Install packages not yet installed
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}

# load packages
invisible(lapply(packages, library, character.only = TRUE))

rm(packages,installed_packages)

#Read in custom R functions located in the wd$funcs directory folder
FUNCS <- list("RegressionResultsTab.R", "ModelPredFrame.R")
invisible(lapply(FUNCS, function(x) source(paste0(wd$funcs,x))))
rm(FUNCS)

```


## Import Data


```{r, label='Import Data', message=FALSE, warning=FALSE, results = 'hide'}

TeoRings_Circ <- read.csv(paste0(wd$data_f,"TeoRings_Circ.csv"))
TeoRings_Oval <- read.csv(paste0(wd$data_f,"TeoRings_Oval.csv"))

#TMP Architecture polygons
Teo_ArchPoly_Data <- invisible(readOGR(paste0(wd$data_f,"Teo_ArchPoly_Data.gpkg")))

#TMP Rings -- Orig, repositioned, rectangular
#RingsPoly <- invisible(readOGR(paste0(wd$data_r,"RingsPoly_Circle.gpkg")))
RingsPoly <- invisible(readOGR(paste0(wd$data_r,"RingsPoly_Oval.gpkg")))

#TMP survey limit polygon
TMP_MapPoly <- invisible(readOGR(paste0(wd$data_r,"TMP_Map_Poly_Extent.gpkg")))


```

# Weighted Kernel Density Map of Pop Density (Figure 3)

```{r}
distm <- 250
cents = gCentroid(Teo_ArchPoly_Data, byid=T)
Teo_ArchPts_Data = SpatialPointsDataFrame(Teo_ArchPoly_Data@data, coords=cents@coords, bbox=Teo_ArchPoly_Data@bbox, proj4string=Teo_ArchPoly_Data@proj4string)
TeoPts_sf = st_as_sf(Teo_ArchPts_Data) %>% dplyr::select(ID,Area_ha,XM_Pop)

buf = gBuffer(Teo_ArchPts_Data, byid=T, id=NULL, width=distm, quadsegs=10, capStyle="ROUND",joinStyle="ROUND", mitreLimit=1.0)
buf_sf = st_as_sf(buf) %>% dplyr::select(ID,Area_ha,XM_Pop)
TMP_MapPoly_sf = st_as_sf(TMP_MapPoly)
RingsPoly_sf = st_as_sf(RingsPoly)

BufInt <-st_intersection(buf_sf,TMP_MapPoly_sf)
#plot(st_geometry(TMP_MapPoly_sf), pch = 3, col = 'red')
#plot(st_geometry(BufInt), add = TRUE)
BufInt$BufArea<-as.numeric(st_area(BufInt))/10000
BufArea <- BufInt$BufArea
rm(buf,buf_sf,BufInt)
pts_agg <- aggregate(TeoPts_sf, TeoPts_sf, FUN = sum, na.rm=T, join = function(x, y) st_is_within_distance(x, y, dist = distm)) #calculate 3km average for all sites
pts_agg$BufArea <- BufArea
pts_agg$RadiusPopDens <- pts_agg$XM_Pop / pts_agg$BufArea
pts_agg_sp = as(pts_agg,Class = "Spatial")

w <- as.owin(TMP_MapPoly)

Teo_ppp <- ppp(x = cents@coords[,1], y = cents@coords[,2], 
    window = w, marks = pts_agg$RadiusPopDens)
#plot(Teo_ppp)


Teo_smooth = Smooth.ppp(X = Teo_ppp, sigma=distm, eps = 10, weights = Teo_ppp$marks, scalekernel=TRUE)
plot(Teo_smooth)

Teo_PopDens = raster(Teo_smooth)
Teo_PopDens = st_as_stars(Teo_PopDens)

Teo_ArchPoly_Data
Low_sf = st_as_sf(Teo_ArchPts_Data) %>% filter(XM_f == "Low")
IM_sf = st_as_sf(Teo_ArchPts_Data) %>% filter(XM_f == "IM")
UncertStat_sf = st_as_sf(Teo_ArchPts_Data) %>% filter(XM_f == "UncertStat")
High_sf = st_as_sf(Teo_ArchPts_Data) %>% filter(XM_f == "High")
CCFeatPoly_sf = st_as_sf(Teo_ArchPoly_Data) %>% filter(XM_group_f == "CCFeat")
AoDPoly_sf = st_as_sf(Teo_ArchPoly_Data) %>% filter(XM_group_f == "AoD")
PlazaPoly_sf = st_as_sf(Teo_ArchPoly_Data) %>% filter(XM_group_f == "Plaza")

  my_breaks <- c(0, 55, 110, floor(max(Teo_smooth$v, na.rm=T)))
  my_labs <- sapply(my_breaks, paste, "/ha", sep="")
  my_breaks[1] <- 1
#plasma inferno cividis viridis     begin = 0.15, 
plt = ggplot() +geom_stars(data = Teo_PopDens)+
  scale_fill_viridis_c(option = "rocket", na.value = NA, 
                       name = paste0(distm,"m Kernel    \nPop Density    "),
                       breaks = my_breaks, labels = my_labs) +
  geom_sf(data = CCFeatPoly_sf, fill=NA, color = "cyan", size=0.3, alpha=0.2) +
  geom_sf(data = AoDPoly_sf, fill=NA, color = "cyan", size=0.3, alpha=0.2) +
  geom_sf(data = PlazaPoly_sf, fill=NA, color = "cyan", size=0.3, alpha=0.2) +
  #geom_sf(data = Low_sf, color="red", size=0.75) +
  #geom_sf(data = UncertStat_sf, color="magenta", size=0.75) +
  #geom_sf(data = IM_sf, color="yellow", size=0.75) +
  #geom_sf(data = High_sf, color="green", size=0.75) +
  geom_sf(data = RingsPoly_sf, fill=NA, color="white", size=1) +
  geom_sf(data = TMP_MapPoly_sf, fill=NA, color="black", size=1.5) +
  coord_sf(datum = sf::st_crs(32614))+
  theme_void() +
  theme(legend.position = "bottom", legend.key.width = unit(2.5, "cm"))+
  theme(legend.title = element_text(size=14, face="bold"))+
  theme(legend.text = element_text(size=12, face="bold"))
plt
ggsave("Fig3_PopDens.png", plot = plt, device = "png", path = wd$figs, scale = 1, width = 7, height = 5,   units = "in",  dpi = 1000, bg = "white")

rm(w,UncertStat_sf,TMP_MapPoly,TMP_MapPoly_sf,TeoPts_sf,Teo_smooth,Teo_ppp,Teo_PopDens,Teo_ArchPts_Data,Teo_ArchPoly_Data,RingsPoly_sf,RingsPoly,pts_agg_sp,pts_agg,PlazaPoly_sf,Low_sf,IM_sf,High_sf,cents,CCFeatPoly_sf,AoDPoly_sf,plt,my_breaks,my_labs,distm,BufArea)
```

pts = data.frame('x'=Teo_ArchPoly_Data@data$East_Poly, 'y' = Teo_ArchPoly_Data@data$North_Poly)
d = duplicated(pts)
z = Teo_ArchPoly_Data@data[,1:8]
pts$dup <- d
pts = cbind(pts,z)


# Population Density Falloff Curve

First, we must fit an exponential function to the falloff population density curve. We will fit a simple exponential model taking the form

$D_{i} = \beta_{1} e^{\beta_{2}d_{i}} + \epsilon$

where $D_{i}$ is the population density of the *i*th concentric ring (in persons per hectare), $d_{i}$ is the median distance of the *i*th concentric ring from the central point (in meters), and $\epsilon$ denotes independent and identically distributed (i.d.d.) Gaussian stochastic variability.
 
```{r Define simple exponential function, include=FALSE,echo=F,message=FALSE,warning=FALSE,results = 'hide'}
expfunc <- function(MedRingDist, b1, b2) {
  b1 * exp( b2 * MedRingDist )
}
```



## Total Population Density

Looking at the data, rings 3-10 seem to follow a tight pattern of exponential decay. However, we can see that the population density of the first two rings do not follow the pattern of exponential decay. As such, we will fit out first model to rings 3-10 only

TeoRings_Circ

geom_smooth(data = TeoRings_Oval, aes(x = MedRingDist, y = Popdens_TOT), se=F,linetype = "solid", color="red2", size=1.3)+

```{r echo=FALSE,message=FALSE,warning=FALSE}

p1 <- ggplot(data = TeoRings_Oval, aes(x = MedRingDist, y = Popdens_TOT, 
                                       xmin = MinRingDist, xmax = MaxRingDist, 
                                       label=Ring)) +
  geom_point(size=2, color="black", shape=16, stroke =2)+
  geom_errorbarh(height=1.5, size=1) +
  geom_text_repel(size=4,direction="y", fontface="bold", nudge_y=2, point.size=5) +#box.padding=1, 
  #geom_text_repel(box.padding=1,size=5,fontface="bold", nudge_y=1.5) +# 
  ggtitle("Total Population Density Gradient for 500-meter Concentric Rings", subtitle= "Teotihuacan, Xolalpan-Metepec Phase (c. AD 350-600)") +
  xlab("Distance from Center (meters)") +
  ylab("Total Pop Density (persons/ha)") +
  theme_bw() +
  #scale_y_continuous(expand = c(0, 0), limits=c(0,90),breaks=seq(0,90,10)) +
  #scale_x_continuous(expand = c(0, 0), limits=c(0,5000),breaks=seq(0,5000,500)) +
  theme(plot.title = element_text(size = 14, face = "bold",hjust = 0.5)) +
  theme(plot.subtitle = element_text(size = 12, face = "bold.italic",hjust = 0.5)) +
  theme(axis.text = element_text(size = 12, color="black")) +
  theme(axis.title.y = element_text(size = 14, face = "bold")) +
  theme(axis.title.x = element_text(size = 14, face = "bold"))

p1 + geom_point(data=TeoRings_Circ, size=2, color="blue", shape=16, stroke =2)

```

```{r include=FALSE,echo=F,message=FALSE,warning=FALSE,results = 'hide'}
#Estimate the model
exp_nls_fit <- nls.multstart::nls_multstart(Popdens_TOT ~ expfunc(MedRingDist, b1, b2),
                             data = TeoRings_Oval[-1,],
                             start_lower = c(b1=250, b2=-1e-2),
                             start_upper = c(b1=350, b2=-1e-4),
                             iter = 500,
                             supp_errors = "Y")

pp = ModelPredFrame(exp_nls_fit,TeoRings_Oval[-1,],"MedRingDist","Popdens_TOT")

```


### Full Regression Results

*"Robust" coef estimates estimated using covariance matrices corrected for heteroskedasticity and autocorrelation*

```{r echo=FALSE,message=FALSE,warning=FALSE}

exp_nls_fit_results = RegressionResultsTab(exp_nls_fit, TeoRings_Oval[-1,], TeoRings_Oval[-1,]$MedRingDist, TeoRings_Oval[-1,]$Popdens_TOT, model_type="nls", coef="both", residplots=TRUE, residhists=TRUE)

exp_nls_fit_results[[1]]
exp_nls_fit_results[[2]]
exp_nls_fit_results[[3]]
```


### Graph the Model

```{r echo=FALSE,message=FALSE,warning=FALSE}

f4a <- ggplot() +
  geom_point(data = TeoRings_Oval, aes(x = MedRingDist, y = Popdens_TOT, xmin = MinRingDist, xmax = MaxRingDist, label=Ring), size=2.5, color="black", shape=16, stroke =2)+
  
  geom_line(data = pp, aes(x=MedRingDist, y=Popdens_TOT.p), inetype = "solid", color="red", size=1.3) +
  #geom_text_repel(data = TeoRings_Oval, aes(x = MedRingDist, y = Popdens_TOT, xmin = MinRingDist, xmax = MaxRingDist, label=Ring), size=4,direction="y", fontface="bold", nudge_y=2, point.size=5) +#box.padding=1, 
  #geom_text_repel(box.padding=1,size=5,fontface="bold", nudge_y=1.5) +# 
   geom_point(data = TeoRings_Oval, aes(x = MedRingDist, y = Popdens_TOT, xmin = MinRingDist, xmax = MaxRingDist, label=Ring), size=2.5, color="black", shape=16, stroke =2)+
  geom_errorbarh(data = TeoRings_Oval, aes(x = MedRingDist, y = Popdens_TOT, xmin = MinRingDist, xmax = MaxRingDist, label=Ring),height=1.5, size=1) +
  #geom_point(data = TeoRings_Oval %>% filter(Ring > 1), aes(x = MedRingDist, y = Popdens_TOT, xmin = MinRingDist, xmax = MaxRingDist, label=Ring), size=2.5, color="black", shape=16, stroke =2)+
  #geom_point(data = TeoRings_Oval %>% filter(Ring < 2), aes(x = MedRingDist, y = Popdens_TOT), size=3, color="red2", shape=4, stroke =2)+
  annotate("label", x = 3000, y = 90, label = "atop(bold(italic(Popdens) == 199.15 * italic(e) ^ (-0.000832 * ~italic(Dist))),bold(italic(pseudo~R^2) == 0.965 ~~~~~~ italic(n) == 8 ))", parse = TRUE, color ="black", size=4)+
  #ggtitle("Total Population Density Gradient for 500-meter Concentric Rings", subtitle= "Teotihuacan, Xolalpan-Metepec Phase (c. AD 350-600)") +
  xlab("Distance from Center (meters)") +
  ylab("Pop Density (per ha)") +
  theme_bw() +
  #scale_y_continuous(expand = c(0, 0), limits=c(0,90),breaks=seq(0,90,10)) +
  scale_x_continuous(expand = c(0, 0), limits=c(-20,4600),breaks=seq(0,4000,1000)) +
  theme(plot.title = element_text(size = 14, face = "bold",hjust = 0.5)) +
  theme(plot.subtitle = element_text(size = 12, face = "bold.italic",hjust = 0.5)) +
  theme(axis.text = element_text(size = 12, color="black")) +
  theme(axis.title.y = element_text(size = 14, face = "bold")) +
  theme(axis.title.x = element_text(size = 14, face = "bold"))
f4a
```

```{r echo=FALSE,message=FALSE,warning=FALSE}

f4b <- ggplot() +
  geom_errorbarh(data = TeoRings_Oval, aes(x = MedRingDist, y = Avg_Area_DStr, xmin = MinRingDist, xmax = MaxRingDist, label=Ring),height=0.0025, size=1) +
  geom_line(data = TeoRings_Oval, aes(x=MedRingDist, y=Avg_Area_DStr), inetype = "solid", color="firebrick", size=1.3) +
  geom_point(data = TeoRings_Oval, aes(x = MedRingDist, y = Avg_Area_DStr, xmin = MinRingDist, xmax = MaxRingDist, label=Ring), size=2.5, color="black", shape=16, stroke =2)+
  
  xlab("Distance from Center (meters)") +
  ylab("Avg Dom Struct Area (ha)") +
  theme_bw() +
  
  scale_y_continuous(labels = scales::percent) +
  scale_x_continuous(expand = c(0, 0), limits=c(-20,4600),breaks=seq(0,4000,1000)) +
  theme(plot.title = element_text(size = 14, face = "bold",hjust = 0.5)) +
  theme(plot.subtitle = element_text(size = 12, face = "bold.italic",hjust = 0.5)) +
  theme(axis.text = element_text(size = 12, color="black")) +
  theme(axis.title.y = element_text(size = 14, face = "bold")) +
  theme(axis.title.x = element_text(size = 14, face = "bold"))
f4b
```

```{r echo=FALSE,message=FALSE,warning=FALSE}

f4c <- ggplot() +
  geom_errorbarh(data = TeoRings_Oval, aes(x = MedRingDist, y = PctRow_Area_Open, xmin = MinRingDist, xmax = MaxRingDist, label=Ring),height=0.01, size=1) +
  geom_line(data = TeoRings_Oval, aes(x=MedRingDist, y=PctRow_Area_Open), inetype = "solid", color="orange2", size=1.3) +
  geom_point(data = TeoRings_Oval, aes(x = MedRingDist, y = PctRow_Area_Open, xmin = MinRingDist, xmax = MaxRingDist, label=Ring), size=2.5, color="black", shape=16, stroke =2)+
  geom_errorbarh(data = TeoRings_Oval, aes(x = MedRingDist, y = PctRow_Area_CCFeat_AoD, xmin = MinRingDist, xmax = MaxRingDist, label=Ring),height=0.01, size=1) +
  geom_line(data = TeoRings_Oval, aes(x=MedRingDist, y=PctRow_Area_CCFeat_AoD), inetype = "solid", color="blue", size=1.3) +
  geom_point(data = TeoRings_Oval, aes(x = MedRingDist, y = PctRow_Area_CCFeat_AoD, xmin = MinRingDist, xmax = MaxRingDist, label=Ring), size=2.5, color="black", shape=16, stroke =2)+
  annotate("label", x = 3000, y = 0.7, label = "% Open Area", color ="orange2", size=7)+
  annotate("label", x = 3000, y = 0.25, label = "% CC Feature Area", color ="blue", size=7)+
  xlab("Distance from Center (meters)") +
  ylab("Percent Area in Ring") +#Open
  theme_bw() +
  scale_y_continuous(labels = scales::percent) +
  scale_x_continuous(expand = c(0, 0), limits=c(-20,4600),breaks=seq(0,4000,1000)) +
  theme(plot.title = element_text(size = 14, face = "bold",hjust = 0.5)) +
  theme(plot.subtitle = element_text(size = 12, face = "bold.italic",hjust = 0.5)) +
  theme(axis.text = element_text(size = 12, color="black")) +
  theme(axis.title.y = element_text(size = 14, face = "bold")) +
  theme(axis.title.x = element_text(size = 14, face = "bold"))
f4c
```
```{r echo=FALSE,message=FALSE,warning=FALSE}

f4d <- ggplot() +
  geom_errorbarh(data = TeoRings_Oval, aes(x = MedRingDist, y = PctRow_Area_Open, xmin = MinRingDist, xmax = MaxRingDist, label=Ring),height=0.01, size=1) +
  geom_line(data = TeoRings_Oval, aes(x=MedRingDist, y=PctRow_Area_Open), inetype = "solid", color="yellowgreen", size=1.3) +
  geom_point(data = TeoRings_Oval, aes(x = MedRingDist, y = PctRow_Area_Open, xmin = MinRingDist, xmax = MaxRingDist, label=Ring), size=2.5, color="black", shape=16, stroke =2)+
  
  xlab("Distance from Center (meters)") +
  ylab("Open % of Ring Area") +
  theme_bw() +
  scale_y_continuous(labels = scales::percent, limits=c(0.3,1), breaks=seq(0.4,1,0.2)) +
  scale_x_continuous(expand = c(0, 0), limits=c(-20,4600),breaks=seq(0,4000,1000)) +
  theme(plot.title = element_text(size = 14, face = "bold",hjust = 0.5)) +
  theme(plot.subtitle = element_text(size = 12, face = "bold.italic",hjust = 0.5)) +
  theme(axis.text = element_text(size = 12, color="black")) +
  theme(axis.title.y = element_text(size = 14, face = "bold")) +
  theme(axis.title.x = element_text(size = 14, face = "bold"))
f4d
```

```{r echo=FALSE,message=FALSE,warning=FALSE}

f4e <- ggplot() +
  geom_errorbarh(data = TeoRings_Oval, aes(x = MedRingDist, y = PctRow_Area_CCFeat_AoD, xmin = MinRingDist, xmax = MaxRingDist, label=Ring),height=0.005, size=1) +
  geom_line(data = TeoRings_Oval, aes(x=MedRingDist, y=PctRow_Area_CCFeat_AoD), inetype = "solid", color="blue", size=1.3) +
  geom_point(data = TeoRings_Oval, aes(x = MedRingDist, y = PctRow_Area_CCFeat_AoD, xmin = MinRingDist, xmax = MaxRingDist, label=Ring), size=2.5, color="black", shape=16, stroke =2)+
  
  xlab("Distance from Center (meters)") +
  ylab(" % Ring Area CC Feat") +
  theme_bw() +
  scale_y_continuous(labels = scales::percent, limits=c(0,0.25), breaks=seq(0,0.25,0.05)) +
  #scale_y_continuous(expand = c(0, 0), limits=c(0,90),breaks=seq(0,90,10)) +
  scale_x_continuous(expand = c(0, 0), limits=c(-20,4600),breaks=seq(0,4000,1000)) +
  theme(plot.title = element_text(size = 14, face = "bold",hjust = 0.5)) +
  theme(plot.subtitle = element_text(size = 12, face = "bold.italic",hjust = 0.5)) +
  theme(axis.text = element_text(size = 12, color="black")) +
  theme(axis.title.y = element_text(size = 14, face = "bold")) +
  theme(axis.title.x = element_text(size = 14, face = "bold"))
f4e
```

```{r Define simple power function, include=FALSE,echo=F,message=FALSE,warning=FALSE,results = 'hide'}
pwrfunc <- function(PctRow_Area_CCFeat_AoD, b1, b2) {
  b1 * PctRow_Area_CCFeat_AoD^b2
}
```

```{r include=FALSE,echo=F,message=FALSE,warning=FALSE,results = 'hide'}
#Estimate the model
pwr_nls_fit <- nls.multstart::nls_multstart(PctRow_Area_Open ~ pwrfunc(PctRow_Area_CCFeat_AoD, b1, b2),
                             data = TeoRings_Oval,
                             start_lower = c(b1=-1, b2=-1),
                             start_upper = c(b1=1, b2=1),
                             iter = 500,
                             supp_errors = "Y")

pp2 = ModelPredFrame(pwr_nls_fit,TeoRings_Oval,"PctRow_Area_CCFeat_AoD","PctRow_Area_Open")

```


### Full Regression Results

*"Robust" coef estimates estimated using covariance matrices corrected for heteroskedasticity and autocorrelation*

```{r echo=FALSE,message=FALSE,warning=FALSE}

pwr_nls_fit_results = RegressionResultsTab(pwr_nls_fit, TeoRings_Oval, TeoRings_Oval$PctRow_Area_CCFeat_AoD, TeoRings_Oval$PctRow_Area_Open, model_type="nls", coef="both", residplots=TRUE, residhists=TRUE)

exp_nls_fit_results[[1]]
exp_nls_fit_results[[2]]
exp_nls_fit_results[[3]]
```

```{r echo=FALSE,message=FALSE,warning=FALSE}

f4f <- ggplot() +
  geom_point(data = TeoRings_Oval, aes(x = PctRow_Area_CCFeat_AoD, y = PctRow_Area_Open), size=2.5, color="black", shape=16, stroke =2)+
  
  geom_line(data = pp2, aes(x=PctRow_Area_CCFeat_AoD, y=PctRow_Area_Open.p), inetype = "solid", color="gold2", size=1.3) +
  #geom_text_repel(data = TeoRings_Oval, aes(x = MedRingDist, y = Popdens_TOT, xmin = MinRingDist, xmax = MaxRingDist, label=Ring), size=4,direction="y", fontface="bold", nudge_y=2, point.size=5) +#box.padding=1, 
  #geom_text_repel(box.padding=1,size=5,fontface="bold", nudge_y=1.5) +# 


  #geom_point(data = TeoRings_Oval %>% filter(Ring > 1), aes(x = MedRingDist, y = Popdens_TOT, xmin = MinRingDist, xmax = MaxRingDist, label=Ring), size=2.5, color="black", shape=16, stroke =2)+
  #geom_point(data = TeoRings_Oval %>% filter(Ring < 2), aes(x = MedRingDist, y = Popdens_TOT), size=3, color="red2", shape=4, stroke =2)+
  annotate("label", x = 0.15, y = 0.8, label = "atop(bold(italic(PctOpen) == 0.914 * ~italic(PctCCFeat) ^ (-5.388)),bold(italic(pseudo~R^2) == 0.771 ~~~~~~ italic(n) == 9 ))", parse = TRUE, color ="black", size=4)+
  #ggtitle("Total Population Density Gradient for 500-meter Concentric Rings", subtitle= "Teotihuacan, Xolalpan-Metepec Phase (c. AD 350-600)") +
  xlab("Percent CC Feature Area in Ring") +
  ylab("Percent Open Area in Ring") +
  theme_bw() +
  scale_y_continuous(labels = scales::percent, limits=c(0.3,1), breaks=seq(0.4,1,0.2)) +
  scale_x_continuous(labels = scales::percent, limits=c(0,0.25), breaks=seq(0,0.25,0.05)) +
  #scale_y_continuous(expand = c(0, 0), ,) +
  #scale_x_continuous(expand = c(0, 0), limits=c(-20,4600),breaks=seq(0,4000,1000)) +
  theme(plot.title = element_text(size = 14, face = "bold",hjust = 0.5)) +
  theme(plot.subtitle = element_text(size = 12, face = "bold.italic",hjust = 0.5)) +
  theme(axis.text = element_text(size = 12, color="black")) +
  theme(axis.title.y = element_text(size = 14, face = "bold")) +
  theme(axis.title.x = element_text(size = 14, face = "bold"))
f4f
```
CCFeat_AoD_Area
Area_Open
```{r}

areas = data.frame("Ring"= TeoRings_Oval$Ring, "MedRingDist"= TeoRings_Oval$MedRingDist, "DomStruct" = (TeoRings_Oval$Area_DStr+TeoRings_Oval$DomPlat_Area), "CCFeat" = TeoRings_Oval$CCFeat_O_Area, "Open" = TeoRings_Oval$Area_OpenUnoccu)
areas = areas %>% pivot_longer(3:5, names_to = "Land_Use", values_to = "Area") %>%
  group_by(Ring, Land_Use) %>%
  summarise(n = sum(Area)) %>%
  mutate(percentage = n / sum(n))
LandUse <- factor(areas$Land_Use, levels = c('Open', 'CCFeat', 'DomStruct'))

f4g <- ggplot(areas, aes(x=Ring, y=percentage, fill=LandUse)) + 
    geom_area(alpha=0.6 , size=1, colour="black",stat="identity")+
  scale_fill_manual(values = c("yellowgreen","blue","firebrick"))+
xlab("Ring") +
  ylab("Percent of Ring Area") +
  theme_bw() +
  scale_y_continuous(labels = scales::percent, limits=c(0,1)) +#expand = c(0, 0), limits=c(0,90),breaks=seq(0,90,10)
  scale_x_continuous(expand = c(0, 0), limits=c(1,9),breaks=seq(1,9,1)) +
  theme(legend.position = c(0.65, 0.5))+
  theme(legend.title = element_text(size=14, face="bold"))+
  theme(legend.text = element_text(size=12, face="bold"))+
  theme(axis.text = element_text(size = 12, color="black")) +
  theme(axis.title.y = element_text(size = 14, face = "bold")) +
  theme(axis.title.x = element_text(size = 14, face = "bold"))
f4g
```




```{r}
plot_grid(
  f4a, f4b, f4c, f4e#,
  #labels = "AUTO", ncol = 2, label_size = 30,
  #label_x = 1, label_y = 1
)
```

```{r}
plot_grid(
  f4a, f4b, 
  labels = "AUTO", ncol = 2, label_size = 30
  #label_x = 1, label_y = 1
)
```


```{r}

areas = data.frame("Ring"= TeoRings_Oval$Ring,
                   "High" = TeoRings_Oval$Elite_DStrArea, 
                   "IM" = TeoRings_Oval$IM_DStrArea, 
                   "Uncertain" = TeoRings_Oval$UncerStat_Area,
                   "Low" = TeoRings_Oval$Low_DStrArea)
areas = areas %>% pivot_longer(2:5, names_to = "Status", values_to = "Area") %>%
  group_by(Ring, Status) %>%
  summarise(n = sum(Area)) %>%
  mutate(percentage = n / sum(n))
Class <- factor(areas$Status, levels = c('High','IM','Uncertain','Low'))

f5a <- ggplot(areas, aes(x=Ring, y=percentage, fill=Class)) + 
    geom_area(alpha=0.6 , size=1, colour="black",stat="identity")+
  scale_fill_manual(values = c("green","yellow","orange","red"))+
xlab("Ring") +
  ylab("% Ring Dom Struct Area") +
  theme_bw() +
  scale_y_continuous(labels = scales::percent, limits=c(0,1)) +#expand = c(0, 0), limits=c(0,90),breaks=seq(0,90,10)
  scale_x_continuous(expand = c(0, 0), limits=c(1,9),breaks=seq(1,9,1)) +
  theme(legend.position = c(0.65, 0.5))+
  theme(legend.title = element_text(size=14, face="bold"))+
  theme(legend.text = element_text(size=12, face="bold"))+
  theme(axis.text = element_text(size = 12, color="black")) +
  theme(axis.title.y = element_text(size = 14, face = "bold")) +
  theme(axis.title.x = element_text(size = 14, face = "bold"))
f5a
```



%>%
  group_by(Ring, Status) %>%
  summarise(n = sum(Area)) %>%
  mutate(percentage = n / sum(n))

```{r echo=FALSE,message=FALSE,warning=FALSE}
areas2 = data.frame("MedRingDist"= TeoRings_Oval$MedRingDist,
                   "High" = TeoRings_Oval$PctCol_DStrArea_Elite, 
                   "IM" = TeoRings_Oval$PctCol_DStrArea_IM, 
                   #"Uncertain" = TeoRings_Oval$PctCol_DStrArea_UncerStat,
                   "Low" = TeoRings_Oval$PctCol_Tot_LowDStrArea)
areas2 = areas2 %>% pivot_longer(2:4, names_to = "Status2", values_to = "Percent") 

Class2 <- factor(areas2$Status2, levels = c('High','IM','Low'))#'Uncertain',


f5b <- ggplot() +
  geom_line(data = areas2, aes(x = MedRingDist, y = Percent, color=Class2), size=1.5)+
  scale_color_manual(name = "Class", values = c("green2","gold","red"))+#"orange2",
  geom_point(data = areas2, aes(x = MedRingDist, y = Percent), size=1.5, color="black", shape=16, stroke =2)+
  xlab("Distance from Center (meters)") +
  ylab("% Class Total Dom Str Area") +
  theme_bw() +
  scale_y_continuous(labels = scales::percent) +#, limits=c(0.3,1), breaks=seq(0.4,1,0.2)
  scale_x_continuous(expand = c(0, 0), limits=c(0,4600),breaks=seq(0,4000,1000)) +
  theme(legend.position = c(0.75, 0.65))+
  theme(legend.title = element_text(size=14, face="bold"))+
  theme(legend.text = element_text(size=12, face="bold"))+
  theme(axis.text = element_text(size = 12, color="black")) +
  theme(axis.title.y = element_text(size = 14, face = "bold")) +
  theme(axis.title.x = element_text(size = 14, face = "bold"))
f5b
```
xlab("Ring") +
  ylab("Percent of Ring Dom Struct Area") +
  theme_bw() +
  scale_y_continuous(labels = scales::percent, limits=c(0,1)) +#expand = c(0, 0), limits=c(0,90),breaks=seq(0,90,10)
  scale_x_continuous(expand = c(0, 0), limits=c(1,9),breaks=seq(1,9,1)) +
  
  theme(axis.text = element_text(size = 12, color="black")) +
  theme(axis.title.y = element_text(size = 14, face = "bold")) +
  theme(axis.title.x = element_text(size = 14, face = "bold"))

```{r echo=FALSE,message=FALSE,warning=FALSE}

f5c <- ggplot(data = TeoRings_Oval, aes(x = PctRow_Area_CCStr, y = PctRow_DStrArea_Elite)) +
  geom_point(size=2.5, color="black", shape=16, stroke =2)+
  geom_smooth(method = lm, se = FALSE,color="green3", size=1.3)+
  annotate("label", x = 0.075, y = 0.44, label = "atop(bold(italic(PctHigh) == 0.39 * ~italic(PctCCFeat) + 0.0047),bold(italic(R^2) == 0.998 ~~~~~~ italic(n) == 9 ))", parse = TRUE, color ="black", size=4)+
  xlab("CC Feat % Ring Area") +
  ylab("High Status % Ring DStr Area") +
  theme_bw() +
  scale_y_continuous(labels = scales::percent) +#, limits=c(0.3,1), breaks=seq(0.4,1,0.2)
  scale_x_continuous(labels = scales::percent) +#, limits=c(0,0.25), breaks=seq(0,0.25,0.05)
  theme(plot.title = element_text(size = 14, face = "bold",hjust = 0.5)) +
  theme(plot.subtitle = element_text(size = 12, face = "bold.italic",hjust = 0.5)) +
  theme(axis.text = element_text(size = 12, color="black")) +
  theme(axis.title.y = element_text(size = 14, face = "bold")) +
  theme(axis.title.x = element_text(size = 14, face = "bold"))
f5c
```


```{r Define simple power function, include=FALSE,echo=F,message=FALSE,warning=FALSE,results = 'hide'}
explinfunc <- function(PctRow_Area_Open, b1, b2) {
  exp((b1*PctRow_Area_Open)+b2)
}
```

```{r include=FALSE,echo=F,message=FALSE,warning=FALSE,results = 'hide'}
#Estimate the model
explin_nls_fit <- nls.multstart::nls_multstart(PctRow_Ring_DStrArea_Low ~ explinfunc(PctRow_Area_Open, b1, b2),
                             data = TeoRings_Oval,
                             start_lower = c(b1=1, b2=-15),
                             start_upper = c(b1=10, b2=1),
                             iter = 500,
                             supp_errors = "Y")

pp3 = ModelPredFrame(explin_nls_fit,TeoRings_Oval,"PctRow_Area_Open","PctRow_Ring_DStrArea_Low")

```


### Full Regression Results

*"Robust" coef estimates estimated using covariance matrices corrected for heteroskedasticity and autocorrelation*

```{r echo=FALSE,message=FALSE,warning=FALSE}

explin_nls_fit_results = RegressionResultsTab(explin_nls_fit, TeoRings_Oval, TeoRings_Oval$PctRow_Area_Open, TeoRings_Oval$PctRow_Ring_DStrArea_Low, model_type="nls", coef="both", residplots=TRUE, residhists=TRUE)

explin_nls_fit_results[[1]]
explin_nls_fit_results[[2]]
explin_nls_fit_results[[3]]
```

```{r echo=FALSE,message=FALSE,warning=FALSE}

f5d <- ggplot() +
  geom_point(data = TeoRings_Oval, aes(x = PctRow_Area_Open, y = PctRow_Ring_DStrArea_Low), size=2.5, color="black", shape=16, stroke =2)+
  
  geom_line(data = pp3, aes(x=PctRow_Area_Open, y=PctRow_Ring_DStrArea_Low.p), inetype = "solid", color="red", size=1.3) +
  #geom_text_repel(data = TeoRings_Oval, aes(x = MedRingDist, y = Popdens_TOT, xmin = MinRingDist, xmax = MaxRingDist, label=Ring), size=4,direction="y", fontface="bold", nudge_y=2, point.size=5) +#box.padding=1, 
  #geom_text_repel(box.padding=1,size=5,fontface="bold", nudge_y=1.5) +# 


  #geom_point(data = TeoRings_Oval %>% filter(Ring > 1), aes(x = MedRingDist, y = Popdens_TOT, xmin = MinRingDist, xmax = MaxRingDist, label=Ring), size=2.5, color="black", shape=16, stroke =2)+
  #geom_point(data = TeoRings_Oval %>% filter(Ring < 2), aes(x = MedRingDist, y = Popdens_TOT), size=3, color="red2", shape=4, stroke =2)+
  annotate("label", x = 0.6, y = 0.04, label = "atop(bold(italic(PctLow) == italic(e) ^ (16.4 * ~italic(PctOpen) - 18.8)),bold(italic(pseudo~R^2) == 0.877 ~~~~~~ italic(n) == 9 ))", parse = TRUE, color ="black", size=4)+
  #ggtitle("Total Population Density Gradient for 500-meter Concentric Rings", subtitle= "Teotihuacan, Xolalpan-Metepec Phase (c. AD 350-600)") +
  xlab("Open % Ring Area") +
  ylab("Low Status % Ring Area") +
  theme_bw() +
  scale_y_continuous(labels = scales::percent) +#, limits=c(0.3,1), breaks=seq(0.4,1,0.2)
  scale_x_continuous(labels = scales::percent) +#, limits=c(0,0.25), breaks=seq(0,0.25,0.05)
  #scale_y_continuous(expand = c(0, 0), ,) +
  #scale_x_continuous(expand = c(0, 0), limits=c(-20,4600),breaks=seq(0,4000,1000)) +
  theme(plot.title = element_text(size = 14, face = "bold",hjust = 0.5)) +
  theme(plot.subtitle = element_text(size = 12, face = "bold.italic",hjust = 0.5)) +
  theme(axis.text = element_text(size = 12, color="black")) +
  theme(axis.title.y = element_text(size = 14, face = "bold")) +
  theme(axis.title.x = element_text(size = 14, face = "bold"))
f5d
```


```{r}
plot_grid(
  f5a, f5b, f5c, f5d#,
  #labels = "AUTO", ncol = 2, label_size = 30
  #label_x = 1, label_y = 1
)
```

```{r}
plot_grid(
  f4a, f4b, f4e, f4g#,
  #labels = "AUTO", ncol = 2, label_size = 30
  #label_x = 1, label_y = 1
)
```


TeoRings_Oval[-1,]

ModelPredFrame
RegressionResultsTab





Combine rings 8 and 9? 
Ring 8 is small and Ring 9 is really small
Constitute outliers in several analyses

In the standard AMM model, an increase in transport costs leads to 
--nucleation
--densification
Sharper increases in 
--prices of land/houses
--building height
--pop density
Sharper decreases in
-dwelling sizes





















