---
title: "Teotihuacan AMM, Script #2:"
subtitle: "Analysis"
author: "Rudolf Cesaretti"
date: "Last run on `r Sys.Date()`"
output:
  html_document:
    toc: true
    df_print: paged
    number_sections: true
---


```{r, setup, include=FALSE,echo=FALSE, message=FALSE,warning=FALSE}
require(knitr)
# Set so that long lines in R will be wrapped:
opts_chunk$set(tidy.opts=list(width.cutoff=75),tidy=TRUE)
#
rm(list = ls())
```


  
# Setup 

All of the data and scripts are downloadable from the [new Teotihuacan AMM Analysis github repository](https://https://github.com/rcesaret/TeotihuacanAMM), which can be cloned to your own account/computer or downloaded directly as a .zip folder.

Either way, once you have done so, you will need to modify the working directory (setwd("C:/...)") path and "dir" variables in the code chunk below to match the repository location on your computer.

```{r, label='Set Local Directory Location', message=FALSE, warning=FALSE}

wd <- list()

#SET YOUR LOCAL DIRECTORY LOCATION HERE:
#wd$dir <- "C:/Users/rcesaret/Dropbox (ASU)/TeotihuacanDean/TeotihuacanAMM/"
wd$dir <- "C:/Users/TJ McMote/Dropbox (ASU)/TeotihuacanDean/TeotihuacanAMM/"

wd$analysis <- paste0(wd$dir,"analysis/")
wd$data_r <- paste0(wd$dir,"data-raw/")
wd$data_p <- paste0(wd$dir,"data-processed/")
wd$data_f <- paste0(wd$dir,"data-final-outputs/")
wd$figs <- paste0(wd$dir,"figures/")
wd$funcs <- paste0(wd$dir,"functions/")

```



## Load R Packages and Custom Functions




```{r, label='Load Libraries', message=FALSE,warning=FALSE}
# Package names
packages <- c("rgdal", "rgeos", "sp", "sf", "GISTools", "raster","stars", "spatstat",
              "tidyverse", "tidyr", "nls.multstart", "nlme", "brms", "broom", 
              "ggrepel", "minpack.lm", "data.table", "zoo", "lmtest", "sandwich", 
              "nlstools", "MASS", "NSM3", "gridExtra", "ggnewscale", "cowplot", 
              "scales", "viridis", "Cairo", "kableExtra")

# Install packages not yet installed
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}

# load packages
invisible(lapply(packages, library, character.only = TRUE))

rm(packages,installed_packages)

#Read in custom R functions located in the wd$funcs directory folder
FUNCS <- list("RegressionResultsTab.R", "ModelPredFrame.R")
invisible(lapply(FUNCS, function(x) source(paste0(wd$funcs,x))))
rm(FUNCS)

```


## Import Data


```{r, label='Import Data', message=FALSE, warning=FALSE, results = 'hide'}

#TeoRings <- read.csv(paste0(wd$data_f,"TeoRings_Circ.csv"))
TeoRings <- read.csv(paste0(wd$data_f,"TeoRings_Oval.csv"))

#TMP Architecture polygons
Teo_ArchPoly_Data <- invisible(readOGR(paste0(wd$data_f,"Teo_ArchPoly_Data.gpkg")))

#TMP Rings -- Orig, repositioned, rectangular
#RingsPoly <- invisible(readOGR(paste0(wd$data_r,"RingsPoly_Circle.gpkg")))
RingsPoly <- invisible(readOGR(paste0(wd$data_r,"RingsPoly_Oval.gpkg")))

#TMP survey limit polygon
TMP_MapPoly <- invisible(readOGR(paste0(wd$data_r,"TMP_Map_Poly_Extent.gpkg")))

#UrbanOpenPoly <- invisible(readOGR(paste0(wd$data_r,"UrbanOpenPoly.gpkg")))
#RuralOpenPoly <- invisible(readOGR(paste0(wd$data_r,"RuralOpenPoly.gpkg")))
TeoUrbanBorder <- invisible(readOGR(paste0(wd$data_r,"TeoUrbanBorder.gpkg")))
TeoUrbanBorder_Inverse <- invisible(readOGR(paste0(wd$data_r,"TeoUrbanBorder_Inverse.gpkg")))

RegressionTable <- data.frame("Figure"=c("X","Y","Form","Equation","Est. Method","R^2","n_rings","n_total","b1 (p)","b2 (p)"), row.names = c("X","Y","Form","Equation","Est. Method","R^2","n_rings","n_total","b1 (p)","b2 (p)"))
RegressionTable <- RegressionTable[,-1]
```





# Figure 3

```{r}
distm <- 125#250

cents = gCentroid(Teo_ArchPoly_Data, byid=T)

Teo_ArchPts_Data = SpatialPointsDataFrame(Teo_ArchPoly_Data@data, coords=cents@coords, bbox=Teo_ArchPoly_Data@bbox, proj4string=Teo_ArchPoly_Data@proj4string)
TeoPts_sf = st_as_sf(Teo_ArchPts_Data) %>% dplyr::select(ID,Area_ha,XM_Pop)

buf = gBuffer(Teo_ArchPts_Data, byid=T, id=NULL, width=distm, quadsegs=10, capStyle="ROUND",joinStyle="ROUND", mitreLimit=1.0)
buf_sf = st_as_sf(buf) %>% dplyr::select(ID,Area_ha,XM_Pop)
TMP_MapPoly_sf = st_as_sf(TMP_MapPoly)
RingsPoly_sf = st_as_sf(RingsPoly) %>% mutate(xx = "500m Rings")

BufInt <-st_intersection(buf_sf,TMP_MapPoly_sf)
#plot(st_geometry(TMP_MapPoly_sf), pch = 3, col = 'red')
#plot(st_geometry(BufInt), add = TRUE)
BufInt$BufArea<-as.numeric(st_area(BufInt))/10000
BufArea <- BufInt$BufArea
rm(buf,buf_sf,BufInt)
pts_agg <- aggregate(TeoPts_sf, TeoPts_sf, FUN = sum, na.rm=T, join = function(x, y) st_is_within_distance(x, y, dist = distm)) #calculate 3km average for all sites
pts_agg$BufArea <- BufArea
pts_agg$RadiusPopDens <- pts_agg$XM_Pop / pts_agg$BufArea
pts_agg_sp = as(pts_agg,Class = "Spatial")

w <- as.owin(TMP_MapPoly)

Teo_ppp <- ppp(x = cents@coords[,1], y = cents@coords[,2], 
    window = w, marks = pts_agg$RadiusPopDens)
#plot(Teo_ppp)


Teo_smooth = Smooth.ppp(X = Teo_ppp, sigma=distm, eps = 10, weights = Teo_ppp$marks, scalekernel=TRUE)
plot(Teo_smooth)

Teo_PopDens = raster(Teo_smooth)

writeRaster(Teo_PopDens, paste0(wd$data_f,"Teo_PopDens"), format= "GTiff", overwrite=TRUE)

#Teo_PopDens
Teo_PopDens = st_as_stars(Teo_PopDens)

TeoUrbanBorder_sf = st_as_sf(TeoUrbanBorder)
TeoUrbanBorder_Inverse_sf = st_as_sf(TeoUrbanBorder_Inverse)
#RuralOpenPoly_sf = st_as_sf(RuralOpenPoly)
Low_sf = st_as_sf(Teo_ArchPts_Data) %>% filter(XM_f == "Low")
IM_sf = st_as_sf(Teo_ArchPts_Data) %>% filter(XM_f == "IM")
UncertStat_sf = st_as_sf(Teo_ArchPts_Data) %>% filter(XM_f == "UncertStat")
High_sf = st_as_sf(Teo_ArchPts_Data) %>% filter(XM_f == "High")
CCFeatPoly_sf = st_as_sf(Teo_ArchPoly_Data) %>% filter(XM_group_f == "CCFeat" | XM_group_f == "AoD" | XM_group_f == "Plaza") %>% mutate(Architecture = "Civic-Ceremonial Features")
#AoDPoly_sf = st_as_sf(Teo_ArchPoly_Data) %>% filter(XM_group_f == "AoD")
#PlazaPoly_sf = st_as_sf(Teo_ArchPoly_Data) %>% filter(XM_group_f == "Plaza")

  
```
                
```{r}
my_breaks <- c(0, 50, 100, floor(max(Teo_smooth$v, na.rm=T)))
  my_labs <- sapply(my_breaks, paste, "/ha", sep="")
  my_breaks[1] <- 1
  
cols <- c("500m Rings" = "gray50", "Civic-Ceremonial Features" = "cyan", "TMP Survey Extent" = "black")
  
map = ggplot() +geom_stars(data = Teo_PopDens)+
  scale_fill_viridis_c(option = "rocket", na.value = NA, direction = -1,
                       name = paste0(distm,"m Smoothed    \nPopulation Density    "),
                       breaks = my_breaks, labels = my_labs) +
  geom_sf(data = TeoUrbanBorder_sf, fill=NA, color = "black", size=1) +
  geom_sf(data = TeoUrbanBorder_Inverse_sf, color=NA, fill = "white", size=0) +
  geom_sf(data = RingsPoly_sf, aes(color=xx), fill=NA, size=1.5) +
  geom_sf(data = CCFeatPoly_sf, aes(color=Architecture), fill=NA, size=0.3,  alpha=0.2, show.legend = "line") +
  scale_colour_manual(name=NULL,values = cols)+
  geom_sf(data = TMP_MapPoly_sf, fill=NA, color="black", size=2) +
  coord_sf(datum = sf::st_crs(32614))+
  theme_void() +
  theme(legend.position = c(0.9,0.8))+
  theme(legend.title = element_text(size=11, face="bold"))+
  theme(legend.text = element_text(size=10, face="bold"))#+
map
ggsave("Fig3.png", plot = map, device = "png", path = wd$figs, scale = 1, width = 10, height = 8,   units = "in",  dpi = 1000, bg = "white")

#rm(w,UncertStat_sf,TMP_MapPoly,TMP_MapPoly_sf,TeoPts_sf,Teo_smooth,Teo_ppp,Teo_PopDens,Teo_ArchPts_Data,Teo_ArchPoly_Data,RingsPoly_sf,RingsPoly,pts_agg_sp,pts_agg,PlazaPoly_sf,Low_sf,IM_sf,High_sf,cents,CCFeatPoly_sf,AoDPoly_sf,my_breaks,my_labs,distm,BufArea,RuralOpenPoly_sf)
```

# Figure 4

## Figure 4A: Population Density Gradient / Falloff Curve

First, we must fit an exponential function to the falloff population density curve. We will fit a simple exponential model taking the form

$D_{i} = \beta_{1} e^{\beta_{2}d_{i}} + \epsilon$

where $D_{i}$ is the population density of the *i*th concentric ring (in persons per hectare), $d_{i}$ is the median distance of the *i*th concentric ring from the central point (in meters), and $\epsilon$ denotes independent and identically distributed (i.d.d.) Gaussian stochastic variability.
 
```{r Define simple exponential function, include=FALSE,echo=F,message=FALSE,warning=FALSE,results = 'hide'}
expfunc <- function(MedRingDist, b1, b2) {
  b1 * exp( b2 * MedRingDist )
}
```

```{r include=FALSE,echo=F,message=FALSE,warning=FALSE,results = 'hide'}
#Estimate the model
fit_f4a <- nls.multstart::nls_multstart(Popdens_BuiltUp ~ expfunc(MedRingDist, b1, b2),
                             data = TeoRings[-1,],
                             start_lower = c(b1=50, b2=-1e-2),
                             start_upper = c(b1=350, b2=-1e-4),
                             iter = 500,
                             supp_errors = "Y")

predict_f4a = ModelPredFrame(fit_f4a,TeoRings[-1,],"MedRingDist","Popdens_BuiltUp")
#RegressionTable
results_f4a = RegressionResultsTab(fit_f4a, TeoRings[-1,], TeoRings[-1,]$MedRingDist, TeoRings[-1,]$Popdens_BuiltUp, model_type="nls", coef="robust", residplots=F, residhists=F)

RegressionTable$`Figure 3A` <- c("Median Distance","Population Density","Exponential","Y = b1 e^(b2*X)",
                    "NLS",paste(round(results_f4a[[1]]$R2,3)), paste(results_f4a[[1]]$n), 
                    paste(sum(TeoRings[-1,]$DStr_TOT, na.rm=T), "(DStr)"),
paste0(round(results_f4a[[2]]$estimate[[1]],3),"\n(p < ",round(results_f4a[[2]]$p.value[[1]],5),")"),
paste0(round(results_f4a[[2]]$estimate[[2]],4),"\n(p < ",round(results_f4a[[2]]$p.value[[2]],7),")"))

```


```{r echo=FALSE,message=FALSE,warning=FALSE}
predict_f4a$Series <- "Population Density"
names(predict_f4a) <- c("X","Y","Series")
f4afactor <- factor(predict_f4a$Series, levels = c("Population Density"))

f4a <- ggplot() +
  geom_point(data = TeoRings, aes(x = MedRingDist, y = Popdens_BuiltUp, xmin = MinRingDist, xmax = MaxRingDist, label=Ring), size=2.5, color="black", shape=16, stroke =2)+
  #geom_line(data = predict_f4a, aes(x=MedRingDist, y=Popdens_BuiltUp.p), inetype = "solid", color="firebrick", size=1.3) +
   geom_line(data = predict_f4a, aes(x=X, y=Y, color=f4afactor), inetype = "solid", size=1.3) +
   geom_point(data = TeoRings, aes(x = MedRingDist, y = Popdens_BuiltUp, xmin = MinRingDist, xmax = MaxRingDist, label=Ring), size=2.5, color="black", shape=16, stroke =2)+
  geom_errorbarh(data = TeoRings, aes(x = MedRingDist, y = Popdens_BuiltUp, xmin = MinRingDist, xmax = MaxRingDist, label=Ring),height=1.5, size=1) +
  #annotate("label", x = 3000, y = 70, label = "atop(bold(italic(PopDens) == 131.8 * italic(e) ^ (-0.00064 * ~italic(Dist))),bold(italic(R^2) == 0.978 ~~~~~~ italic(n) == 8 ))", parse = TRUE, color ="black", size=5)+
  #annotate("label", x = 3000, y = 60, label = "Population Density", color ="firebrick", size=5)+
  scale_color_manual(name = "", values = c("firebrick"), labels=c("Population Density"))+
  xlab("Distance from Center (km)") +
  ylab("Population Density (per ha)") +
  theme_bw() +
  scale_y_continuous(expand = c(0, 0), limits=c(0,85), breaks=seq(10,70,20)) +
  scale_x_continuous(expand = c(0, 0), limits=c(-20,4600),breaks=seq(0,4000,1000),
                     labels=function(x)x/1000) +
  theme(plot.title = element_text(size = 14, face = "bold",hjust = 0.5)) +
  theme(plot.subtitle = element_text(size = 12, face = "bold.italic",hjust = 0.5)) +
  theme(legend.position = c(0.6, 0.7))+
  theme(legend.title = element_blank())+
  theme(legend.text = element_text(size=12, face="bold"))+
  theme(legend.key = element_rect(colour = "transparent", fill = "transparent"))+
  theme(legend.background = element_rect(fill="transparent", colour = "transparent"))+
  theme(axis.text = element_text(size = 12, color="black")) +
  theme(axis.title.y = element_text(size = 14, face = "bold")) +
  theme(axis.title.x = element_text(size = 14, face = "bold"))
f4a
```


### Full Regression Results

*"Robust" coef estimates estimated using covariance matrices corrected for heteroskedasticity and autocorrelation*

```{r echo=FALSE,message=FALSE,warning=FALSE}

results_f4a = RegressionResultsTab(fit_f4a, TeoRings[-1,], TeoRings[-1,]$MedRingDist, TeoRings[-1,]$Popdens_BuiltUp, model_type="nls", coef="both", residplots=TRUE, residhists=TRUE)

results_f4a[[1]]
results_f4a[[2]]
results_f4a[[3]]


```


















## Figure 4B: CC-Feature and Land Use Intensity Gradients

```{r include=FALSE,echo=F,message=FALSE,warning=FALSE,results = 'hide'}
#Estimate the model
fit_f4b <- nls.multstart::nls_multstart(PctRow_Area_ArchFeat ~ expfunc(MedRingDist, b1, b2),
                             data = TeoRings,
                             start_lower = c(b1=0, b2=-1),
                             start_upper = c(b1=1, b2=-1e-8),
                             iter = 500,
                             supp_errors = "Y")

predict_f4b = ModelPredFrame(fit_f4b,TeoRings,"MedRingDist","PctRow_Area_ArchFeat")

results_f4b = RegressionResultsTab(fit_f4b, TeoRings, TeoRings$MedRingDist, TeoRings$PctRow_Area_ArchFeat, model_type="nls", coef="both", residplots=F, residhists=F)

RegressionTable$`Figure 3B` <- c("Median Distance","Arch Feat % Row Area","Exponential","Y = b1 e^(b2*X)",
                    "NLS",paste(round(results_f4b[[1]]$R2,3)), paste(results_f4b[[1]]$n), 
                    paste(sum(TeoRings$ArchFeat_TOT, na.rm=T), "(ArchFeat)"),
paste0(round(results_f4b[[2]]$estimate[[1]],3),"\n(p < ",round(results_f4b[[2]]$p.value[[1]],10),")"),
paste0(round(results_f4b[[2]]$estimate[[2]],4),"\n(p < ",round(results_f4b[[2]]$p.value[[2]],7),")"))

```


```{r echo=FALSE,message=FALSE,warning=FALSE}

predict_f4b$Series <- "All Architectural Features"
names(predict_f4b) <- c("X","Y","Series")
tmp=TeoRings %>% dplyr::select(MedRingDist,PctRow_Area_CCFeat_AoD)
tmp$Series <- "Civic-Ceremonial Features"
names(tmp) <- c("X","Y","Series")
predict_f4b = rbind(predict_f4b,tmp)

f4bfactor <- factor(predict_f4b$Series, levels = c("All Architectural Features", "Civic-Ceremonial Features"))



f4b <- ggplot() +
  geom_errorbarh(data = TeoRings, aes(x = MedRingDist, y = PctRow_Area_CCFeat_AoD, xmin = MinRingDist, xmax = MaxRingDist, label=Ring),height=0.015, size=1) +
  geom_errorbarh(data = TeoRings, aes(x = MedRingDist, y = PctRow_Area_ArchFeat, xmin = MinRingDist, xmax = MaxRingDist, label=Ring),height=0.015, size=1) +
  geom_point(data = TeoRings, aes(x = MedRingDist, y = PctRow_Area_ArchFeat, xmin = MinRingDist, xmax = MaxRingDist, label=Ring), size=2.5, color="black", shape=16, stroke =2)+
  geom_line(data = predict_f4b, aes(x=X, y=Y, color=f4bfactor), inetype = "solid", size=1.3) +
  scale_color_manual(name = "", values = c("purple","blue"), labels=c("All Architectural Features\n(Land Use Intensity)", "Civic-Ceremonial Features"))+
  #geom_line(data = TeoRings, aes(x=MedRingDist, y=PctRow_Area_CCFeat_AoD), inetype = "solid", color="blue", size=1.6) +
  geom_point(data = TeoRings, aes(x = MedRingDist, y = PctRow_Area_CCFeat_AoD, xmin = MinRingDist, xmax = MaxRingDist, label=Ring), size=2.5, color="black", shape=16, stroke =2)+
  
  #geom_errorbarh(data = TeoRings, aes(x = MedRingDist, y = PctCol_Area_CCFeat_AoD, xmin = MinRingDist, xmax = MaxRingDist, label=Ring),height=0.015, size=1) +
  #geom_line(data = TeoRings, aes(x=MedRingDist, y=PctCol_Area_CCFeat_AoD), inetype = "solid", color="cyan3", size=1.6) +
  #geom_point(data = TeoRings, aes(x = MedRingDist, y = PctCol_Area_CCFeat_AoD, xmin = MinRingDist, xmax = MaxRingDist, label=Ring), size=2.5, color="black", shape=16, stroke =2)+

  
  #geom_line(data = predict_f4b, aes(x=MedRingDist, y=PctRow_Area_ArchFeat.p), inetype = "solid", color="purple", size=1.3) +
  
  
  #annotate("label", x = 2875, y = 0.62, label = "— Architectural Features  \n   (Land Use Intensity)   ", color ="purple", size=5, face = "bold")+
  #annotate("label", x = 2875, y = 0.50, label = "atop(bold(italic(PctArchFeat) == 0.825 * italic(e) ^ (-0.0008 * ~italic(Dist))),bold(italic(pseudo~R^2) == 0.988 ~~~~~~ italic(n) == 9 ))", parse = TRUE, color ="purple3", size=4)+
    
  #annotate("label", x = 2875, y = 0.4, label = "— % of Total CC Feat Area", color ="cyan4", size=5, face = "bold")+
  #annotate("label", x = 2875, y = 0.4, label = "— Civic-Ceremonial Features", color ="blue", size=5, face = "bold")+
    
  xlab("Distance from Center (km)") +
  ylab("% of Ring Area") +
  theme_bw() +
  scale_y_continuous(labels = scales::percent) +#, limits=c(0,0.25), breaks=seq(0,0.25,0.05)
  #scale_y_continuous(expand = c(0, 0), limits=c(0,90),breaks=seq(0,90,10)) +
  scale_x_continuous(expand = c(0, 0), limits=c(-20,4600),breaks=seq(0,4000,1000),
                     labels=function(x)x/1000) +
  theme(plot.title = element_text(size = 14, face = "bold",hjust = 0.5)) +
  theme(plot.subtitle = element_text(size = 12, face = "bold.italic",hjust = 0.5)) +
  theme(legend.position = c(0.6, 0.7))+
  theme(legend.title = element_blank())+
  theme(legend.text = element_text(size=12, face="bold"))+
  theme(legend.key = element_rect(colour = "transparent", fill = "transparent"))+
  theme(legend.background = element_rect(fill="transparent", colour = "transparent"))+
  theme(axis.text = element_text(size = 12, color="black")) +
  theme(axis.title.y = element_text(size = 14, face = "bold")) +
  theme(axis.title.x = element_text(size = 14, face = "bold"))
f4b
```



### Full Regression Results

*"Robust" coef estimates estimated using covariance matrices corrected for heteroskedasticity and autocorrelation*

```{r echo=FALSE,message=FALSE,warning=FALSE}

results_f4b = RegressionResultsTab(fit_f4b, TeoRings, TeoRings$MedRingDist, TeoRings$PctRow_Area_ArchFeat, model_type="nls", coef="both", residplots=TRUE, residhists=TRUE)

results_f4b[[1]]
results_f4b[[2]]
results_f4b[[3]]
```





## Plot Figure 4

```{r}
Fig4 <- plot_grid(f4a, f4b, labels = "AUTO", label_size = 40, hjust=0)


Fig4

ggsave("Fig4.png", plot = Fig4, device = "png", path = wd$figs, scale = 1, width = 12, height = 5.5,   units = "in",  dpi = 1000, bg = "white")

#rm(f4a, f4b, Fig4)
```















# Figure 5: Land Use Gradients 


## Figure 5A: Stacked area chart of major land use categories in each concentric ring


```{r}

areas = data.frame("Ring"= TeoRings$Ring, "MedRingDist"= TeoRings$MedRingDist, "DomStruct" = (TeoRings$Area_DStr+TeoRings$DomPlat_Area), "CCFeat" = TeoRings$CCFeat_O_Area, "UrbanOpen" = (TeoRings$Area_UrbanOpen + TeoRings$UnOccuFeat_Area), "RuralOpen" = TeoRings$Area_RuralOpen)
areas = areas %>% pivot_longer(3:6, names_to = "Land_Use", values_to = "Area") %>%
  group_by(Ring, Land_Use) %>%
  summarise(n = sum(Area)) %>%
  mutate(percentage = n / sum(n))
LandUse <- factor(areas$Land_Use, levels = c("RuralOpen", "UrbanOpen", 'CCFeat', 'DomStruct'))

f5a <- ggplot(areas, aes(x=Ring, y=percentage, fill=LandUse)) + 
    geom_area(alpha=0.6 , size=1, colour="black",stat="identity")+
  scale_fill_manual(name="Land Use Classes", values = c("yellowgreen","tan","blue","firebrick"),
                    labels=c("Non-Urban Open", "Urban Open", "CC Features", "Domestic Structures"))+
xlab("Concentric Ring") +
  ylab("% Ring Area") +
  theme_bw() +
  scale_y_continuous(labels = scales::percent) +#, limits=c(0,1)expand = c(0, 0), limits=c(0,90),breaks=seq(0,90,10)
  scale_x_continuous(expand = c(0, 0), limits=c(1,9),breaks=seq(1,9,1)) +
  theme(legend.position = c(0.775, 0.75))+
  theme(legend.title = element_text(size=12, face="bold"))+
  theme(legend.text = element_text(size=10, face="bold"))+
  theme(legend.background = element_rect(color=alpha('white', 0.5), fill=alpha('white', 0.5)))+
  theme(axis.text = element_text(size = 12, color="black")) +
  theme(axis.title.y = element_text(size = 14, face = "bold")) +
  theme(axis.title.x = element_text(size = 14, face = "bold"))
f5a
```

## Figure 5B

```{r}

areas = data.frame("Ring"= TeoRings$Ring,
                   "High" = TeoRings$Elite_DStrArea, 
                   "Intermediate" = TeoRings$IM_DStrArea, 
                   "Uncertain" = TeoRings$UncerStat_Area,
                   "Low" = TeoRings$Low_DStrArea)
areas = areas %>% pivot_longer(2:5, names_to = "Status", values_to = "Area") %>%
  group_by(Ring, Status) %>%
  summarise(n = sum(Area)) %>%
  mutate(percentage = n / sum(n))
Class <- factor(areas$Status, levels = c('High','Intermediate','Uncertain','Low'))

f5b <- ggplot(areas, aes(x=Ring, y=percentage, fill=Class)) + 
    geom_area(alpha=0.6 , size=1, colour="black",stat="identity")+
  scale_fill_manual(name="Class Status",values = c("green","yellow","orange","red"))+
xlab("Concentric Ring") +
  ylab("% Ring DStr Area") +
  theme_bw() +
  scale_y_continuous(labels = scales::percent, limits=c(0,1)) +#expand = c(0, 0), limits=c(0,90),breaks=seq(0,90,10)
  scale_x_continuous(expand = c(0, 0), limits=c(1,9),breaks=seq(1,9,1)) +
  theme(legend.position = c(0.75, 0.65))+
  theme(legend.title = element_text(size=14, face="bold"))+
  theme(legend.text = element_text(size=12, face="bold"))+
  theme(legend.background = element_rect(color=alpha('white', 0.5), fill=alpha('white', 0.5)))+
  theme(axis.text = element_text(size = 12, color="black")) +
  theme(axis.title.y = element_text(size = 14, face = "bold")) +
  theme(axis.title.x = element_text(size = 14, face = "bold"))
f5b
```

## Figure 5C



```{r echo=FALSE,message=FALSE,warning=FALSE}
Dareas = data.frame("MedRingDist"= TeoRings$MedRingDist,
                    "MinRingDist"= TeoRings$MinRingDist,
                    "MaxRingDist"= TeoRings$MaxRingDist,
                    "Total" = TeoRings$Avg_Area_DStr,
                   "High" = TeoRings$Avg_Elite_DStrArea, 
                   "Intermediate" = TeoRings$Avg_IM_DStrArea, 
                   "Uncertain" = TeoRings$Avg_UncerStat_DStrArea,
                   "Low" = TeoRings$Med_Low_DStrArea *10
                   )
Dareas[5:9,5] <- NA
Dareas[8:9,7] <- NA
Dareas[1,7] <- NA
Dareas = Dareas %>% pivot_longer(4:8, names_to = "Status2", values_to = "AvgDStrArea") 

Class3 <- factor(Dareas$Status2, levels = c('Total', 'High','Intermediate','Uncertain','Low'))#'',


f5c <- ggplot() +
  #geom_errorbarh(data = Dareas, aes(x = MedRingDist, y = AvgDStrArea, xmin = MinRingDist, xmax = MaxRingDist),height=0.75, size=1) +
  geom_line(data = Dareas, aes(x = MedRingDist, y = AvgDStrArea, color=Class3), size=1.5)+
  scale_color_manual(values = c("black","green2","gold","darkorange", "red"), labels=c('Total', 'High','Intermediate','Uncertain', 'Low x 10'))+#"orange2",name = "Avg DStr Area",
  geom_point(data = Dareas, aes(x = MedRingDist, y = AvgDStrArea), size=1.5, color="black", shape=16, stroke =2)+
  xlab("Concentric Ring") +
  ylab("Avg DStr Area (m^2)") +
  theme_bw() +
  scale_y_continuous(expand = c(0, 0), limits=c(0,3300),breaks=seq(0,3000,1000)) +#, limits=c(0.3,1), breaks=seq(0.4,1,0.2)
  scale_x_continuous(expand = c(0, 0), limits=c(0,4600),breaks=seq(0,4000,1000),labels=function(x)x/1000) +
  theme(legend.position = c(0.775, 0.775))+
  theme(legend.title = element_blank())+
  theme(legend.text = element_text(size=11, face="bold"))+
  theme(legend.spacing.y = unit(0.2, 'cm'))+
  theme(legend.key = element_rect(colour = "transparent", fill = "transparent"))+
  theme(legend.background = element_rect(fill="transparent", colour = "transparent"))+
  theme(axis.text = element_text(size = 12, color="black")) +
  theme(axis.title.y = element_text(size = 14, face = "bold")) +
  theme(axis.title.x = element_text(size = 14, face = "bold"))
f5c
```




## Plot Figure 5

plot_grid(
  plot_grid(p1, p2, nrow = 1, ncol = 2),
  plot_grid(NULL, p3, NULL, nrow = 1, rel_widths = c(0.5, 1, 0.5)),
  nrow = 2
)
f5bottom <- plot_grid(f5b, f6c, nrow = 1, ncol = 2, labels = c("B", "C"), label_size = 30, hjust=0)

f5top <- plot_grid(NULL, f5a, NULL,  nrow = 1, ncol = 2, rel_widths = c(0.35, 1.3, 0.35), labels = c("", "A  ", ""), label_size = 30)

#Fig5 <- plot_grid(f5a, f5bottom, nrow = 2, ncol = 1, labels = c('A', ''), label_size = 30, hjust=0)
Fig5 <- plot_grid(f5top, f5bottom, nrow = 2, ncol = 1, hjust=0)
```{r}

Fig5 <- plot_grid(
  plot_grid(f5a, f5b, nrow = 1, ncol = 2, labels = c("A", "B"), label_size = 30, hjust=0),
  plot_grid(NULL, f5c, NULL, nrow = 1, labels = c("", "C", ""), label_size = 30, label_x = -0.025, label_y = 1, rel_widths = c(0.4, 1.2, 0.4)),
  nrow = 2
)

Fig5

ggsave("Fig5.png", plot = Fig5, device = "png", path = wd$figs, scale = 1, width = 10, height = 9,   units = "in",  dpi = 1000, bg = "white")


#rm(f5a, f5b, f5c, Fig5)
```




# Figure 6: Evidence for a Land Value Gradient 


## Figure 6A: High Status Residencies


```{r include=FALSE,echo=F,message=FALSE,warning=FALSE,results = 'hide'}
#Estimate the model
TeoRings <- TeoRings %>% mutate(Log_PctRow_Area_CCFeat_AoD = log(PctRow_Area_CCFeat_AoD),
                                Log_PctRow_DStrArea_Elite = log(PctRow_DStrArea_Elite))

fit_f6a = lm(Log_PctRow_DStrArea_Elite ~ Log_PctRow_Area_CCFeat_AoD, TeoRings[1:6,])



predict_f6a = ModelPredFrame(fit_f6a,TeoRings[1:6,],"Log_PctRow_Area_CCFeat_AoD","Log_PctRow_DStrArea_Elite",unlog_after = T)

results_f6a = RegressionResultsTab(fit_f6a, TeoRings[1:6,], TeoRings$Log_PctRow_Area_CCFeat_AoD, TeoRings$Log_PctRow_DStrArea_Elite, model_type="ols", coef="both", residplots=F, residhists=F)

RegressionTable$`Figure 5A` <- c("Log CC Feat % Ring Area","Log High Stat % DStr Area","Log-Log","log(Y) = b2*log(X) + b1",
                    "OLS",paste(round(results_f6a[[1]]$R2,3)), paste(results_f6a[[1]]$n), 
                    #paste(sum(TeoRings$ArchFeat_TOT, na.rm=T), "(ArchFeat)"),
                    paste(sum(TeoRings[1:6,]$CCStr, na.rm=T), "(CCStr);", sum(TeoRings[1:6,]$Elite_DStr, na.rm=T), "(High DStr)"),
paste0(round(results_f6a[[2]]$estimate[[1]],4),"\n(p < ",round(results_f6a[[2]]$p.value[[1]],4),")"),
paste0(round(results_f6a[[2]]$estimate[[2]],4),"\n(p < ",round(results_f6a[[2]]$p.value[[2]],4),")"))

```



```{r echo=FALSE,message=FALSE,warning=FALSE}
predict_f6a$Series <- "High Status Residencies"
names(predict_f6a) <- c("X","Y","Series")
f6afactor <- factor(predict_f6a$Series, levels = c("High Status Residencies"))


f6a <- ggplot() +
  geom_point(data = TeoRings, aes(x = PctRow_Area_CCFeat_AoD, y = PctRow_DStrArea_Elite),size=2.5, color="black", shape=16, stroke =2)+
     geom_line(data = predict_f6a, aes(x=X, y=Y, color=f6afactor), inetype = "solid", size=1.3) +
scale_color_manual(name = "", values = c("green3"), labels=c("High Status Residencies"))+
  #geom_line(data = predict_f6a, aes(x=Log_PctRow_Area_CCFeat_AoD, y=Log_PctRow_DStrArea_Elite.p), inetype = "solid", color="green3", size=1.3) +
  #geom_smooth(method = lm, se = FALSE,color="green3", size=1.3)+
  #annotate("label", x = 0.065, y = 0.4, label = "atop(bold(italic(PctHigh) == 0.39 * ~italic(PctCCFeat) + 0.005),bold(italic(R^2) == 0.998 ~~~~~~ italic(n) == 9 ))", parse = TRUE, color ="green4", size=4)+
  #annotate("label", x = 0.065, y = 0.46, label = "High Status", color ="green3", size=5)+
  #ggtitle("\nHigh Status Residencies")+
  xlab("CC Feat % Ring Area") +
  ylab("% Ring DStr Area") +
  theme_bw() +
  scale_y_continuous(labels = scales::percent) +#, limits=c(0.3,1), breaks=seq(0.4,1,0.2)
  scale_x_continuous(labels = scales::percent) +#, limits=c(0,0.25), breaks=seq(0,0.25,0.05)
  #theme(plot.title = element_text(size = 14, face = "bold",hjust = 0.5, color="green4")) +
  #theme(plot.subtitle = element_text(size = 12, face = "bold.italic",hjust = 0.5)) +
  theme(legend.position = c(0.3, 0.7))+
  theme(legend.title = element_blank())+
  theme(legend.text = element_text(size=12, face="bold"))+
  theme(legend.key = element_rect(colour = "transparent", fill = "transparent"))+
  theme(legend.background = element_rect(fill="transparent", colour = "transparent"))+
  theme(axis.text = element_text(size = 12, color="black")) +
  theme(axis.title.y = element_text(size = 14, face = "bold")) +
  theme(axis.title.x = element_text(size = 14, face = "bold"))
f6a
```


### Full Regression Results

*"Robust" coef estimates estimated using covariance matrices corrected for heteroskedasticity and autocorrelation*

```{r echo=FALSE,message=FALSE,warning=FALSE}

results_f6a = RegressionResultsTab(fit_f6a, TeoRings[1:6,], TeoRings$Log_PctRow_Area_CCFeat_AoD, TeoRings$Log_PctRow_DStrArea_Elite, model_type="ols", coef="both", residplots=T, residhists=T)

results_f6a[[1]]
results_f6a[[2]]
results_f6a[[3]]
```

## Figure 6B: Intermediate + Uncertain Status Residences


```{r include=FALSE,echo=F,message=FALSE,warning=FALSE,results = 'hide'}
#Estimate the model


fit_f6b1 = lm(PctRow_DStrArea_IM ~ PctRow_Area_CCFeat_AoD, TeoRings)
predict_f6b1 = ModelPredFrame(fit_f6b1,TeoRings,"PctRow_Area_CCFeat_AoD","PctRow_DStrArea_IM")
results_f6b1 = RegressionResultsTab(fit_f6b1, TeoRings, TeoRings$PctRow_Area_CCFeat_AoD, TeoRings$PctRow_DStrArea_IM, model_type="ols", coef="both", residplots=F, residhists=F)

RegressionTable$`Figure 5B-1` <- c("CC Feat % Ring Area","IM Stat % DStr Area","Linear","Y = b2*X + b1",
                    "OLS",paste(round(results_f6b1[[1]]$R2,3)), paste(results_f6b1[[1]]$n), 
                    #paste(sum(TeoRings$ArchFeat_TOT, na.rm=T), "(ArchFeat)"),
                    paste(sum(TeoRings$CCStr, na.rm=T), "(CCFeat);", sum(TeoRings$IM_DStr, na.rm=T), "(IM DStr)"),
paste0(round(results_f6b1[[2]]$estimate[[1]],4),"\n(p < ",round(results_f6b1[[2]]$p.value[[1]],15),")"),
paste0(round(results_f6b1[[2]]$estimate[[2]],4),"\n(p < ",round(results_f6b1[[2]]$p.value[[2]],8),")"))




TeoRings$PctRow_DStrArea_IMUncerStat = TeoRings$PctRow_DStrArea_UncerStat + TeoRings$PctRow_DStrArea_IM

fit_f6b2 = lm(PctRow_DStrArea_IMUncerStat ~ PctRow_Area_CCFeat_AoD, TeoRings)
predict_f6b2 = ModelPredFrame(fit_f6b2,TeoRings,"PctRow_Area_CCFeat_AoD","PctRow_DStrArea_IMUncerStat")
results_f6b2 = RegressionResultsTab(fit_f6b2, TeoRings, TeoRings$PctRow_Area_CCFeat_AoD, TeoRings$PctRow_DStrArea_IMUncerStat, model_type="ols", coef="both", residplots=F, residhists=F)

RegressionTable$`Figure 5B-2` <- c("CC Feat % Ring Area","IM+Uncert Stat % DStr Area","Linear","Y = b2*X + b1",
                    "OLS",paste(round(results_f6b2[[1]]$R2,3)), paste(results_f6b2[[1]]$n), 
                    #paste(sum(TeoRings$ArchFeat_TOT, na.rm=T), "(ArchFeat)"),
                    paste(sum(TeoRings$CCStr, na.rm=T), "(CCFeat);", sum((TeoRings$IM_DStr + TeoRings$UncerStat_DStr), na.rm=T), "(IM+Uncert DStr)"),
paste0(round(results_f6b2[[2]]$estimate[[1]],4),"\n(p < ",round(results_f6b2[[2]]$p.value[[1]],15),")"),
paste0(round(results_f6b2[[2]]$estimate[[2]],4),"\n(p < ",round(results_f6b2[[2]]$p.value[[2]],8),")"))


```


```{r echo=FALSE,message=FALSE,warning=FALSE}
predict_f6b2$Series <- "Intermediate + Uncertain Status"
predict_f6b1$Series <- "Intermediate Status"
names(predict_f6b1) <- c("X","Y","Series")
names(predict_f6b2) <- c("X","Y","Series")
predict_f6b = rbind(predict_f6b1,predict_f6b2)

f6bfactor <- factor(predict_f6b$Series, levels = c("Intermediate Status", "Intermediate + Uncertain Status"))


f6b <- ggplot() +
  geom_point(data = TeoRings, aes(x = PctRow_Area_CCFeat_AoD, y = PctRow_DStrArea_IMUncerStat), size=2.5, color="orange3", shape=16, stroke =2)+
  geom_point(data = TeoRings, aes(x = PctRow_Area_CCFeat_AoD, y = PctRow_DStrArea_IM), size=2.5, color="gold2", shape=16, stroke =2)+
  #geom_line(data = predict_f6b, aes(x=PctRow_Area_CCFeat_AoD, y=PctRow_DStrArea_IM.p), inetype = "solid", color="yellow3", size=1.3) +
  
  geom_line(data = predict_f6b, aes(x=X, y=Y, color=f6bfactor), inetype = "solid", size=1.3) +
  scale_color_manual(name = "", values = c("yellow3","darkorange"), labels=c("Intermediate Status", "Intermediate + Uncertain Status"))+
  #geom_smooth(data = TeoRings, aes(x = PctRow_Area_CCFeat_AoD, y = PctRow_DStrArea_IMUncerStat), method = lm, se = FALSE,color="darkorange", size=1.3)+
  #annotate("label", x = 0.155, y = 0.915, label = "atop(bold(italic(PctIMU) == -1.95 * ~italic(PctCCFeat) + 0.98),bold(italic(R^2) == 0.98 ~~~~~~ italic(n) == 9 ))", parse = TRUE, color ="orange4", size=4)+
  #annotate("label", x = 0.155, y = 0.975, label = "Intermediate + Uncertain Status", color ="darkorange", size=5)+
  
  
  #geom_smooth(data = TeoRings, aes(x = PctRow_Area_CCFeat_AoD, y = PctRow_DStrArea_IM), method = lm, se = FALSE,color="yellow3", size=1.3)+
  
  #annotate("label", x = 0.08, y = 0.55, label = "atop(bold(italic(PctIM) == -1.55 * ~italic(PctCCFeat) + 0.88),bold(italic(R^2) == 0.938 ~~~~~~ italic(n) == 9 ))", parse = TRUE, color ="yellow4", size=4)+
  #annotate("label", x = 0.08, y = 0.615, label = "Intermediate Status", color ="yellow3", size=5)+
  #ggtitle("\nIntermediate Status Residencies")+
  xlab("CC Feat % Ring Area") +
  ylab("% Ring DStr Area") +
  theme_bw() +
  scale_y_continuous(labels = scales::percent, limits=c(0.5,1), breaks=seq(0.5,0.9,0.2)) +#
  scale_x_continuous(labels = scales::percent) +#, limits=c(0,0.25), breaks=seq(0,0.25,0.05)
  #theme(plot.title = element_text(size = 14, face = "bold",hjust = 0.5, color="gold3")) +
  #theme(plot.subtitle = element_text(size = 12, face = "bold.italic",hjust = 0.5)) +
  theme(legend.position = c(0.6, 0.9))+
  theme(legend.title = element_blank())+
  theme(legend.text = element_text(size=12, face="bold"))+
  theme(legend.key = element_rect(colour = "transparent", fill = "transparent"))+
  theme(legend.background = element_rect(fill="transparent", colour = "transparent"))+
  theme(axis.text = element_text(size = 12, color="black")) +
  theme(axis.title.y = element_text(size = 14, face = "bold")) +
  theme(axis.title.x = element_text(size = 14, face = "bold"))
f6b
```


### Full Regression Results


#### Intermediate Status Only


```{r}
results_f6b1 = RegressionResultsTab(fit_f6b1, TeoRings, TeoRings$PctRow_Area_CCFeat_AoD, TeoRings$PctRow_DStrArea_IM, model_type="ols", coef="both", residplots=T, residhists=T)
results_f6b1[[1]]
results_f6b1[[2]]
results_f6b1[[3]]
```

#### Intermediate + Uncertain Status

```{r}
results_f6b2 = RegressionResultsTab(fit_f6b2, TeoRings, TeoRings$PctRow_Area_CCFeat_AoD, TeoRings$PctRow_DStrArea_IM, model_type="ols", coef="both", residplots=T, residhists=T)
results_f6b2[[1]]
results_f6b2[[2]]
results_f6b2[[3]]
```




## Figure 6C: Low Status Residences

```{r include=FALSE,echo=F,message=FALSE,warning=FALSE,results = 'hide'}
#Estimate the model
TeoRings <- TeoRings %>% mutate(Log_PctRow_Ring_DStr_Low = log(PctRow_Ring_DStr_Low))

fit_f6c = lm(Log_PctRow_Ring_DStr_Low ~ Log_PctRow_Area_CCFeat_AoD, TeoRings)



predict_f6c = ModelPredFrame(fit_f6c,TeoRings,"Log_PctRow_Area_CCFeat_AoD","Log_PctRow_Ring_DStr_Low",unlog_after = T)#, xmin = log(0.002)

results_f6c = RegressionResultsTab(fit_f6c, TeoRings, TeoRings$Log_PctRow_Area_CCFeat_AoD, TeoRings$Log_PctRow_Ring_DStr_Low, model_type="ols", coef="both", residplots=F, residhists=F)

RegressionTable$`Figure 5C` <- c("Log CC Feat % Ring Area","Log Low Stat % DStr","Log-Log","log(Y) = b2*log(X) + b1",
                    "OLS",paste(round(results_f6c[[1]]$R2,3)), paste(results_f6c[[1]]$n), 
                    #paste(sum(TeoRings$ArchFeat_TOT, na.rm=T), "(ArchFeat)"),
                    paste(sum(TeoRings$CCStr, na.rm=T), "(CCStr);", sum(TeoRings$Low_DStr, na.rm=T), "(Low DStr)"),
paste0(round(results_f6c[[2]]$estimate[[1]],4),"\n(p < ",round(results_f6c[[2]]$p.value[[1]],4),")"),
paste0(round(results_f6c[[2]]$estimate[[2]],4),"\n(p < ",round(results_f6c[[2]]$p.value[[2]],4),")"))

```


```{r echo=FALSE,message=FALSE,warning=FALSE}
predict_f6c$Series <- "Low Status Residencies"
names(predict_f6c) <- c("X","Y","Series")
f6cfactor <- factor(predict_f6c$Series, levels = c("Low Status Residencies"))


f6c <- ggplot() +
  geom_point(data = TeoRings, aes(x = PctRow_Area_CCFeat_AoD, y = PctRow_Ring_DStr_Low), size=2.5, color="black", shape=16, stroke =2)+
  geom_line(data = predict_f6c, aes(x=X, y=Y, color=f6cfactor), inetype = "solid", size=1.3) +
  scale_color_manual(name = "", values = c("red"), labels=c("Low Status Residencies"))+
  #geom_line(data = predict_f6c, aes(x=Log_PctRow_Area_CCFeat_AoD, y=Log_PctRow_Ring_DStr_Low.p), inetype = "solid", color="red", size=1.3) +
  #annotate("label", x = 0.125, y = 0.4, label = "Low Status", color ="red", size=5)+
  #annotate("label", x = 0.125, y = 0.04, label = "atop(bold(italic(PctCCFeat) == 0.00000679 ~italic(PctLow) ^ -1.47),bold(italic(pseudo~R^2) == 0.995 ~~~~~~ italic(n) == 9 ))", parse = TRUE, color ="firebrick", size=4)+
  #ggtitle("\nLow Status Residencies")+
  xlab("CC Feat % Ring Area") +
  ylab("% Ring DStr") +
  theme_bw() +
  scale_y_continuous(labels = scales::percent) +#, breaks=seq(0.4,1,0.2)
  scale_x_continuous(labels = scales::percent) +#, limits=c(0,0.25), breaks=seq(0,0.25,0.05)
  theme(legend.position = c(0.6, 0.7))+
  theme(legend.title = element_blank())+
  theme(legend.text = element_text(size=12, face="bold"))+
  theme(legend.key = element_rect(colour = "transparent", fill = "transparent"))+
  theme(legend.background = element_rect(fill="transparent", colour = "transparent"))+
  #scale_y_continuous(expand = c(0, 0), ,) +
  #scale_x_continuous(expand = c(0, 0), limits=c(-20,4600),breaks=seq(0,4000,1000)) +
  theme(plot.title = element_text(size = 14, face = "bold",hjust = 0.5,color="red3")) +
  theme(plot.subtitle = element_text(size = 12, face = "bold.italic",hjust = 0.5)) +
  theme(axis.text = element_text(size = 12, color="black")) +
  theme(axis.title.y = element_text(size = 14, face = "bold")) +
  theme(axis.title.x = element_text(size = 14, face = "bold"))

f6c
```

### Full Regression Results


```{r}
results_f6c = RegressionResultsTab(fit_f6c, TeoRings,TeoRings$Log_PctRow_Area_CCFeat_AoD,  TeoRings$Log_PctRow_Ring_DStr_Low, model_type="ols", coef="both", residplots=T, residhists=T)
results_f6c[[1]]
results_f6c[[2]]
results_f6c[[3]]
```


## Figure 6D: All Architectural Features 


```{r include=FALSE,echo=F,message=FALSE,warning=FALSE,results = 'hide'}



fit_f6d = lm(PctRow_Area_ArchFeat ~ Log_PctRow_Area_CCFeat_AoD, TeoRings)



predict_f6d = ModelPredFrame(fit_f6d,TeoRings,"Log_PctRow_Area_CCFeat_AoD","PctRow_Area_ArchFeat",unlog_after_x = T)#, xmin = log(0.002)

results_f6d = RegressionResultsTab(fit_f6d, TeoRings, TeoRings$Log_PctRow_Area_CCFeat_AoD, TeoRings$PctRow_Area_ArchFeat, model_type="ols", coef="both", residplots=F, residhists=F)

RegressionTable$`Figure 5D` <- c("Log CC Feat % Ring Area","Arch Feat % Area","Log-X","X = b2*log(Y) + b1",
                    "OLS",paste(round(results_f6d[[1]]$R2,3)), paste(results_f6d[[1]]$n), 
                    #paste(sum(TeoRings$ArchFeat_TOT, na.rm=T), "(ArchFeat)"),
                    paste(sum(TeoRings$CCStr, na.rm=T), "(CCStr);", sum(TeoRings$ArchFeat_TOT, na.rm=T), "(Arch Feat)"),
paste0(round(results_f6d[[2]]$estimate[[1]],4),"\n(p < ",round(results_f6d[[2]]$p.value[[1]],4),")"),
paste0(round(results_f6d[[2]]$estimate[[2]],4),"\n(p < ",round(results_f6d[[2]]$p.value[[2]],4),")"))

```


```{r echo=FALSE,message=FALSE,warning=FALSE}

predict_f6d$Series <- "All Architectural Features"
names(predict_f6d) <- c("X","Y","Series")
f6dfactor <- factor(predict_f6d$Series, levels = c("All Architectural Features"))

f6d <- ggplot() +
  geom_point(data = TeoRings, aes(x = PctRow_Area_CCFeat_AoD, y = PctRow_Area_ArchFeat), size=2.5, color="black", shape=16, stroke =2)+
  #geom_line(data = predict_f6d, aes(x=Log_PctRow_Area_CCFeat_AoD, y=PctRow_Area_ArchFeat.p), inetype = "solid", color="purple", size=1.3) +
  geom_line(data = predict_f6d, aes(x=X, y=Y, color=f6dfactor), inetype = "solid", size=1.3) +
  scale_color_manual(name = "", values = c("purple"), labels=c("All Architectural Features"))+
  #annotate("label", x = 0.125, y = 0.26, label = "All Architectural Features", color ="purple", size=5)+
  #annotate("label", x = 0.125, y = 0.17, label = "atop(bold(italic(PctArchFeat) == 0.144 ~italic(PctCCFeat) + 0.847),bold(italic(R^2) == 0.819 ~~~~~~ italic(n) == 9 ))", parse = TRUE, color ="purple3", size=4)+
  #ggtitle("\nAll Architectural Features")+
  xlab("CC Feat % Ring Area") +
  ylab("Arch Feat % Ring Area  ") +
  theme_bw() +
  scale_y_continuous(labels = scales::percent) +#, breaks=seq(0.4,1,0.2)
  scale_x_continuous(labels = scales::percent) +#, limits=c(0,0.25), breaks=seq(0,0.25,0.05)
  theme(legend.position = c(0.7, 0.35))+
  theme(legend.title = element_blank())+
  theme(legend.text = element_text(size=12, face="bold"))+
  theme(legend.key = element_rect(colour = "transparent", fill = "transparent"))+
  theme(legend.background = element_rect(fill="transparent", colour = "transparent"))+
  scale_y_continuous(labels = scales::percent, limits=c(0,0.7),breaks=c(0, 0.2, 0.4, 0.6)) +
  scale_x_continuous(labels = scales::percent) +
  #theme(plot.title = element_text(size = 14, face = "bold",hjust = 0.5,color="purple3")) +
  #theme(plot.subtitle = element_text(size = 12, face = "bold.italic",hjust = 0.5)) +
  theme(axis.text = element_text(size = 12, color="black")) +
  theme(axis.title.y = element_text(size = 14, face = "bold")) +
  theme(axis.title.x = element_text(size = 14, face = "bold"))

f6d
```


### Full Regression Results


```{r}
results_f6d = RegressionResultsTab(fit_f6d, TeoRings, TeoRings$Log_PctRow_Area_CCFeat_AoD, TeoRings$PctRow_Area_ArchFeat, model_type="ols", coef="both", residplots=T, residhists=T)
results_f6d[[1]]
results_f6d[[2]]
results_f6d[[3]]
```




## Plot Figure 5

```{r}
Fig6 <- plot_grid(f6a, f6b, f6c, f6d, labels = "AUTO", label_size = 30, hjust=-1)


Fig6


ggsave("Fig6.png", plot = Fig6, device = "png", path = wd$figs, scale = 1, width = 10, height = 8,   units = "in",  dpi = 1000, bg = "white")






#rm(f6a, f6b, f6c, f6d, Fig6)
```





# Regression Table

```{r 'Regression Table', echo=FALSE, message=FALSE, warning=FALSE}
RegressionTable.t <- tibble(RegressionTable)
# Table of Variable Definitions for Ring Data
RegressionTable.t %>% 
  #dplyr::select(Column:Description) %>%
  kable(booktabs = TRUE) %>% #, align=c('c','l','l','l')
  #group_rows(index = table(TeoRingsVars$Set)) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))



```


```{r}
write.csv(RegressionTable, paste0(wd$data_f,"RegressionTable.csv"))
```





