---
title: "Teotihuacan AMM, Script #1:"
subtitle: "Data Prep and Dataset Construction"
author: "Rudolf Cesaretti"
date: "Last run on `r Sys.Date()`"
output:
  html_document:
    toc: true
    df_print: paged
    number_sections: true
bibliography: References.bib
csl: apa.csl
link-citations: yes
---

```{css, echo=FALSE}
pre {
  max-height: 300px;
  overflow-y: auto;
}

pre[class] {
  max-height: 300px;
}
```

```{r, setup, include=FALSE,echo=FALSE, message=FALSE,warning=FALSE}
require(knitr)
# Set so that long lines in R will be wrapped:
opts_chunk$set(tidy.opts=list(width.cutoff=75),tidy=TRUE)
#
rm(list = ls())
```

This R markdown document : 
Topographic/environmental metrics

  1. Calculate catchment area variables, including
      + Topographic/environmental metrics
      + 
  4. Reorganize the data and export for Script #6
  
  
# Setup 

All of the data and scripts are downloadable from the [new Teotihuacan AMM Analysis github repository](https://https://github.com/rcesaret/ASUSettlementPersist2022), which can be cloned to your own account/computer or downloaded directly as a .zip folder.

Either way, once you have done so, you will need to modify the working directory (setwd("C:/...)") path and "dir" variables in the code chunk below to match the repository location on your computer.

```{r, label='Set Local Directory Location', message=FALSE,warning=FALSE}

wd <- list()

#SET YOUR LOCAL DIRECTORY LOCATION HERE:
#wd$dir <- "C:/Users/rcesaret/Dropbox (ASU)/TeotihuacanDean/TeotihuacanAMM/"
wd$dir <- "C:/Users/TJ McMote/Dropbox (ASU)/TeotihuacanDean/TeotihuacanAMM/"

wd$analysis <- paste0(wd$dir,"analysis/")
wd$data_r <- paste0(wd$dir,"data-raw/")
wd$data_p <- paste0(wd$dir,"data-processed/")
wd$data_f <- paste0(wd$dir,"data-final-outputs/")
wd$figs <- paste0(wd$dir,"figures/")
wd$funcs <- paste0(wd$dir,"functions/")

```


## Load R Packages and Custom Functions

```{r, label='Load Libraries', message=FALSE,warning=FALSE}
# Package names
packages <- c("rgdal", "rgeos", "sp", "sf", "GISTools", "raster", 
              "tidyverse", "tidyr", "ggnewscale", "cowplot")
              # "spatialEco","purrr","stars","data.table", "Matrix", "gdistance", "lwgeom", 

# Install packages not yet installed
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}

# load packages
invisible(lapply(packages, library, character.only = TRUE))

rm(packages,installed_packages)

#Read in custom R functions located in the wd$funcs directory folder
FUNCS <- list("HelperFunctions.R", "CalcRingData.R")
invisible(lapply(FUNCS, function(x) source(paste0(wd$funcs,x))))
rm(FUNCS)

```





## Import Data

Data we are importing:

  1. TeoArchDataPts.csv
  2. TMPArchAnalysis_v3_5.6.22.gpkg
  3. TMP survey limit polygon
  4. TMP Rings
  5. Rivers
  6. Raster Basemap
  7. Points for labels on maps

EXPLAIN WHAT EACH FILE IS

Refer to metadata


The primary class spatial data format used in this script is the Spatial Polygon Dataframe (spdf) class from the “sp” R package. While I frequently switch back-and-forth to the “Simple Features” (sf) class from the “sf” R package data, I make sure to revert to Spatial Polygon Dataframe (spdf) after all sf calculations.

We will be working in the coordinate reference system (CRS; projection) WGS84 / UTM Zone 14N (ESPG:32614) for the entirety of this analysis.



  2. A simple polygon calculated in QGIS that specifies a hard outer border for the catchment areas of sites (constructed for sensitivity to survey borders and sites not included in the SBOM sample)
  3. Cost-distance matrices from script #3
  4. A raster hillshade basemap for the SBOM which includes the lakes

```{r, label='Import Data', message=FALSE, warning=FALSE}

#TMP Architectural interpretation points
TeoArch_Pts <- read.csv(paste0(wd$data_r,"TeoArchDataPts.csv"))

#TMP Architecture polygons
TeoArch_Poly <- readOGR(paste0(wd$data_r,"TMPArchPoly.gpkg"))

#Added Open Space Arch Features
# <- readOGR(paste0(wd$data_r,".gpkg"))

#TMP Rings -- Orig, repositioned, rectangular
RingsPoly_Circle <- readOGR(paste0(wd$data_r,"RingsPoly_Circle.gpkg"))
RingsPoly_Oval <- readOGR(paste0(wd$data_r,"RingsPoly_Oval.gpkg"))

#TMP survey limit polygon
TMP_MapPoly <- readOGR(paste0(wd$data_r,"TMP_Map_Poly_Extent.gpkg"))


#TMP raster basemap
#Rivers



```


## Variables


### Architectural Classifications

TABLE


## Data Integration


```{r label='Reorganize Data', message=FALSE,warning=FALSE}


## Modify some existing variables
#RingsPoly_Oval@data$Dist <- as.numeric(RingsPoly_Oval@data$Dist)
names(TeoArch_Pts)[names(TeoArch_Pts) == 'Area_ha'] <- 'Area_ha_Pts'
names(TeoArch_Pts)[names(TeoArch_Pts) == 'Area_m2'] <- 'Area_m2_Pts'
names(TeoArch_Pts)[names(TeoArch_Pts) == 'Ring'] <- 'Ring_Circle'
TeoArch_Poly@data$FID_1 <- as.numeric(TeoArch_Poly@data$FID_1)
names(TeoArch_Poly@data)[names(TeoArch_Poly@data) == 'FID_1'] <- 'ID'
names(TeoArch_Poly@data)[names(TeoArch_Poly@data) == 'Area_m2USE'] <- 'Area_m2'
names(TeoArch_Poly@data)[names(TeoArch_Poly@data) == 'EastUSE'] <- 'East_Poly'
names(TeoArch_Poly@data)[names(TeoArch_Poly@data) == 'NorthUSE'] <- 'North_Poly'
names(TeoArch_Poly@data)[names(TeoArch_Poly@data) == 'Ring'] <- 'Ring_Oval'


## Calculate Area_ha for TeoArch_Poly@data
TeoArch_Poly@data$Area_ha <- TeoArch_Poly@data$Area_m2 / 10000

## Check to see if the data match perfectly:
x = as.numeric(TeoArch_Pts$ID)
y = as.numeric(TeoArch_Poly@data$ID)
validate1 <- setdiff(x,y)
validate2 <- setdiff(y,x)

## If the data match perfectly, merge the point and polygon data

if (length(validate1) == 0 & length(validate2) == 0){
  
  Teo_Poly_Data <- sp::merge(TeoArch_Poly, TeoArch_Pts, by="ID")
  
  #TeoArch_Poly <- TeoArch_Poly[order(TeoArch_Poly$ID),]
  #TeoArch_Pts <- TeoArch_Pts[order(TeoArch_Pts$ID),]
  #identical(TeoArch_Pts$ID, TeoArch_Poly@data$ID)

  Teo_Poly_Data.sf <- st_as_sf(Teo_Poly_Data)
  #writeOGR(Teo_Poly_Data, paste0(wd$data_p,"TMPArchPoly_Data.gpkg"), 
  #         "TMPArchPoly_Data", driver = "GPKG", overwrite_layer = T)
  
  rm(x,y,validate1,validate2)#TeoArch_Pts, TeoArch_Poly)
  
} else {
  paste("Point data and polygon data do not match perfectly!")
}

```




# Classification of Open Space


--cut open space into polys by ring, given 

THIS GOES AFTER DATA INTEGRATION
--Integrate again --> another file that contains the open space classes


```{r label='', message=FALSE,warning=FALSE}

```


# Calculating Concentric Ring Data


## Alternative Ring Layouts


maps side-by-side to show difference

```{r, 'comparrison maps of ring variants', echo=FALSE, message=FALSE,warning=FALSE}

RingsPoly_Oval.sf <- st_as_sf(RingsPoly_Oval)
RingsPoly_Circle.sf <- st_as_sf(RingsPoly_Circle)
TMP_MapPoly.sf <- st_as_sf(TMP_MapPoly)

p_circ = ggplot() + 
  geom_sf(data = Teo_Poly_Data.sf, aes(geometry = geometry),color="black", size=0.1, fill="blue") +
  geom_sf(data = RingsPoly_Circle.sf, aes(geometry = geometry), color="red", size=1, alpha = 0) +
  geom_sf(data = TMP_MapPoly.sf, aes(geometry = geometry), color="black", size=1.1, alpha = 0) +
  labs(title= "Circular 500-meter Rings",subtitle="Center = Point = In front of Sun Pyramid")+
  coord_sf()+
  theme_void()+
  theme(plot.title = element_text(hjust = 0.5, face="bold", size=16),
        plot.subtitle = element_text(hjust = 0.5, face="bold", size=12),
        plot.background = element_rect(fill = "white", colour = NA))

p_oval = ggplot() + 
  geom_sf(data = Teo_Poly_Data.sf, aes(geometry = geometry),color="black", size=0.1, fill="blue") +
  geom_sf(data = RingsPoly_Oval.sf, aes(geometry = geometry), color="red", size=1, alpha = 0) +
  geom_sf(data = TMP_MapPoly.sf, aes(geometry = geometry), color="black", size=1.1, alpha = 0) +
  labs(title= "Oval 500-meter Rings",subtitle="Center = Line = Avenue of the Dead")+
  coord_sf()+
  theme_void()+
  theme(plot.title = element_text(hjust = 0.5, face="bold", size=16),
        plot.subtitle = element_text(hjust = 0.5, face="bold", size=12),
        plot.background = element_rect(fill = "white", colour = NA))

compare_rings <- plot_grid(p_circ, p_oval)
compare_rings
rm(RingsPoly_Oval.sf,RingsPoly_Circle.sf,p_circ,p_oval,compare_rings,TMP_MapPoly.sf)
```


## Create Ring Datasets

```{r label='', message=FALSE,warning=FALSE}

## Calculate Circular Rings Data

TeoRings_Circ <- CalcRingData(PolyData = Teo_Poly_Data,
                              RingsPoly = RingsPoly_Circle,
                              RingVersion = "Ring_Circle",
                              output_arch_data = F,
                              output_ring_data = T)

## Calculate Oval Rings Data

TeoRings_Oval <- CalcRingData(PolyData = Teo_Poly_Data,
                              RingsPoly = RingsPoly_Oval,
                              RingVersion = "Ring_Oval",
                              output_arch_data = T,
                              output_ring_data = T)

## Save List output items as separate objects
Teo_ArchPoly_Data <- TeoRings_Oval[[2]]
TeoRings_Oval <- TeoRings_Oval[[1]]


```



# Calc Rings

## Choose Ring Layout

```{r}

RingVersion <- "Ring_Oval"
#RingVersion <- "Ring_Circle"

if (RingVersion == "Ring_Oval") {
  nrings <- nrow(RingsPoly_Oval@data)
  RingsPoly <- RingsPoly_Oval
}

if (RingVersion == "Ring_Circle") {
  nrings <- nrow(RingsPoly_Circle@data)
  RingsPoly <- RingsPoly_Circle
}

```


## Calculate Helper Variables

```{r label='Calculate Helper Variables', message=FALSE, warning=FALSE}

#Create binary land use classification helper variables

Teo_Poly_Data@data <- Teo_Poly_Data@data %>%  mutate(
            XM_OB_bi = ifelse(XM_c == 1, 1, 0),
            XM_Low_bi = ifelse(XM_c == 1, 1, 0),
            XM_IM_bi = ifelse(XM_c == 2, 1, 0),
            XM_UncertStat_bi = ifelse(XM_c == 3, 1, 0),
            XM_High_bi = ifelse(XM_c == 4, 1, 0),
            XM_PlatOther_bi = ifelse(XM_c == 5, 1, 0),
            XM_Altar_bi = ifelse(XM_c == 6, 1, 0),
            XM_PlatformRelig_bi = ifelse(XM_c == 9, 1, 0),
            XM_Religious_bi = ifelse(XM_c == 10, 1, 0),
            XM_ProbTemple_bi = ifelse(XM_c == 16, 1, 0),
            XM_Civic_bi = ifelse(XM_c == 17, 1, 0),
            XM_AoD_bi = ifelse(XM_c == 18, 1, 0),
            XM_Plaza_bi = ifelse(XM_c == 28, 1, 0),
            XM_Other_bi = ifelse(XM_c == 99, 1, 0),
            XM_Unk_bi = ifelse(XM_c == 100, 1, 0),
            XM_Unoccu_bi = ifelse(XM_c == -2, 1, 0),
            XM_grp_OB_bi = ifelse(XM_group_c == 0, 1, 0),
            XM_grp_Low_bi = ifelse(XM_group_c == 1, 1, 0),
            XM_grp_IM_bi = ifelse(XM_group_c == 2, 1, 0),
            XM_grp_UncertStat_bi = ifelse(XM_group_c == 3, 1, 0),
            XM_grp_High_bi = ifelse(XM_group_c == 4, 1, 0),
            XM_grp_DomPlat_bi = ifelse(XM_group_c == 5, 1, 0),
            XM_grp_CCFeat_bi = ifelse(XM_group_c == 6, 1, 0),
            XM_grp_AoD_bi = ifelse(XM_group_c == 7, 1, 0),
            XM_grp_Plaza_bi = ifelse(XM_group_c == 9, 1, 0),
            XM_grp_Other_bi = ifelse(XM_group_c == 10, 1, 0),
            XM_grp_Unk_bi = ifelse(XM_c == 11, 1, 0),
            XM_grp_Unoccu_bi = ifelse(XM_c == 12, 1, 0),
            XM_macro_OB_bi = ifelse(XM_macro_c == 0, 1, 0),
            XM_macro_DStr_bi = ifelse(XM_macro_c == 1, 1, 0),
            XM_macro_DomPlat_bi = ifelse(XM_macro_c == 2, 1, 0),
            XM_macro_CCFeatO_bi = ifelse(XM_macro_c == 3, 1, 0),
            XM_macro_Unk_bi = ifelse(XM_macro_c == 4, 1, 0),
            XM_macro_Unoccu_bi = ifelse(XM_macro_c == 5, 1, 0))

#sum(is.na(TeoDataPts_Rings[,36:227]))

Teo_Poly_Data@data <- Teo_Poly_Data@data %>%  mutate(
    XM_Pop_Low = XM_Low_bi * XM_Pop,
    XM_Area_Low = XM_Low_bi * Area_m2,
    XM_Pop_IM = XM_IM_bi * XM_Pop,
    XM_Area_IM = XM_IM_bi * Area_m2,
    XM_Pop_High = XM_High_bi * XM_Pop,
    XM_Area_High = XM_High_bi * Area_m2,
    XM_Pop_UncertStat = XM_UncertStat_bi * XM_Pop,
    XM_Area_UncertStat = XM_UncertStat_bi * Area_m2)

Teo_Poly_Data@data <- Teo_Poly_Data@data %>%  mutate(
    XM_Area_CCFeat = XM_grp_CCFeat_bi * Area_m2,
    XM_Area_CCFeatO = XM_macro_CCFeatO_bi * Area_m2,
    XM_Area_DStr = XM_macro_DStr_bi * Area_m2,
    XM_Area_OB = XM_grp_OB_bi * Area_m2,
    XM_Area_Unoccu = XM_macro_Unoccu_bi * Area_m2,
    XM_Area_DomPlat = XM_grp_DomPlat_bi * Area_m2,
    XM_Area_Unk = XM_macro_Unk_bi * Area_m2,
    XM_Pop = XM_Pop_Low + XM_Pop_IM + XM_Pop_High + XM_Pop_UncertStat)

```



## Summarize Data By Ring

```{r label='', message=FALSE,warning=FALSE}
my_mean <- function(x) mean(x[x != 0],na.rm = TRUE)
my_median <- function(x) median(x[x != 0],na.rm = TRUE)

Teo_Rings <- Teo_Poly_Data@data %>%
  group_by(!!sym(RingVersion)) %>%
  summarise(
    Pop_TOT = sum(XM_Pop, na.rm=T),
    DStr_TOT = sum(XM_macro_DStr_bi, na.rm=T),
    Area_DStr = sum(XM_Area_DStr, na.rm=T) * 0.0001,
    NonCC_Feat_TOT = sum(XM_macro_Unoccu_bi, na.rm=T) + sum(XM_macro_Unk_bi, na.rm=T) + sum(XM_macro_DStr_bi, na.rm=T) + sum(XM_macro_DomPlat_bi, na.rm=T) + sum(XM_macro_OB_bi, na.rm=T),
    
    NonCC_Feat_Area = (sum(XM_Area_Unoccu, na.rm=T) + sum(XM_Area_Unk, na.rm=T) + sum(XM_Area_DStr, na.rm=T) + sum(XM_Area_OB, na.rm=T) + sum(XM_Area_DomPlat, na.rm=T)) * 0.0001,
    
    NonCCDStr_TOT = sum(XM_macro_Unoccu_bi, na.rm=T) + sum(XM_macro_Unk_bi, na.rm=T) + sum(XM_macro_DomPlat_bi, na.rm=T) + sum(XM_macro_OB_bi, na.rm=T),

    NonCCDStr_Area = (sum(XM_Area_Unoccu, na.rm=T) + sum(XM_Area_Unk, na.rm=T) + sum(XM_Area_OB, na.rm=T) + sum(XM_Area_DomPlat, na.rm=T)) * 0.0001,

    OB = sum(XM_grp_OB_bi, na.rm=T),
    OB_Area = sum(XM_Area_OB, na.rm=T) * 0.0001,
    Unoccu = sum(XM_macro_Unoccu_bi, na.rm=T),
    Unoccu_Area = sum(XM_Area_Unoccu, na.rm=T) * 0.0001,
    DomPlat = sum(XM_macro_DomPlat_bi, na.rm=T),
    DomPlat_Area = sum(XM_Area_DomPlat, na.rm=T) * 0.0001,
    Unk = sum(XM_macro_Unk_bi, na.rm=T),
    Unk_Area = sum(XM_Area_Unk, na.rm=T) * 0.0001,
    CCStr = sum((XM_grp_CCFeat_bi), na.rm=T),
    CCStrArea = sum(XM_Area_CCFeat, na.rm=T) * 0.0001,
    AoD = sum(XM_grp_AoD_bi, na.rm=T),
    AoD_Area = sum((XM_grp_AoD_bi * Area_m2), na.rm=T) * 0.0001,
    Plazas = sum(XM_Plaza_bi, na.rm=T),
    Plaza_Area = sum((XM_Plaza_bi * Area_m2), na.rm=T) * 0.0001,
    PlazAoD_O = sum(XM_Plaza_bi, na.rm=T) + sum(XM_grp_AoD_bi, na.rm=T),
    PlazAoD_O_Area = (sum((XM_Plaza_bi * Area_m2), na.rm=T) + sum((XM_grp_AoD_bi * Area_m2), na.rm=T)) * 0.0001,
    CCFeat_AoD_Area = (sum((XM_grp_AoD_bi * Area_m2), na.rm=T) + sum(XM_Area_CCFeat, na.rm=T))* 0.0001,
    CCFeat_O_Area = sum(XM_Area_CCFeatO, na.rm=T) * 0.0001,
    
    UnOccuFeat = sum(NonCCDStr_TOT, na.rm=T),
    UnOccuFeat_Area = sum(NonCCDStr_Area, na.rm=T) * 0.0001,
    
    Elite_DStr = sum(XM_grp_High_bi, na.rm=T),
    Elite_Pop = sum(XM_Pop_High, na.rm=T),
    Elite_DStrArea = sum(XM_Area_High, na.rm=T) * 0.0001,
    Avg_Elite_DStrArea = my_mean(XM_Area_High) * 0.0001,
    Med_Elite_DStrArea = my_median(XM_Area_High) * 0.0001,
    Avg_Elite_DStrPop = my_mean(XM_Pop_High),
    IM_DStr = sum(XM_grp_IM_bi, na.rm=T),
    IM_Pop = sum(XM_Pop_IM, na.rm=T),
    IM_DStrArea = sum(XM_Area_IM, na.rm=T) * 0.0001,
    Avg_IM_DStrArea = my_mean(XM_Area_IM) * 0.0001,
    Med_IM_DStrArea = my_median(XM_Area_IM) * 0.0001,
    Avg_IM_DStrPop = my_mean(XM_Pop_IM),
    Low_DStr = sum(XM_grp_Low_bi, na.rm=T),
    Low_Pop = sum(XM_Pop_Low, na.rm=T),
    Low_DStrArea = sum(XM_Area_Low, na.rm=T) * 0.0001,
    Avg_Low_DStrArea = my_mean(XM_Area_Low) * 0.0001,
    Med_Low_DStrArea = my_median(XM_Area_Low) * 0.0001,
    Avg_Low_DStrPop = my_mean(XM_Pop_Low),
    UncerStat_DStr = sum(XM_grp_UncertStat_bi, na.rm=T),
    UncerStat_Pop = sum(XM_Pop_UncertStat, na.rm=T),
    UncerStat_Area = sum(XM_Area_UncertStat, na.rm=T) * 0.0001,
    Avg_UncerStat_DStrArea = my_mean(XM_Area_UncertStat) * 0.0001,
    Med_UncerStat_DStrArea = my_median(XM_Area_UncertStat) * 0.0001,
    Avg_UncerStat_DStrPop = my_mean(XM_Pop_UncertStat))
    
#Teo_Rings = Teo_Rings[-c(1,12),]
Teo_Rings$Avg_Elite_DStrArea[is.nan(Teo_Rings$Avg_Elite_DStrArea)]<-0
Teo_Rings$Med_Elite_DStrArea[is.nan(Teo_Rings$Med_Elite_DStrArea)]<-0
Teo_Rings$Avg_Elite_DStrPop[is.nan(Teo_Rings$Avg_Elite_DStrPop)]<-0
Teo_Rings$Avg_IM_DStrArea[is.nan(Teo_Rings$Avg_IM_DStrArea)]<-0
Teo_Rings$Med_IM_DStrArea[is.nan(Teo_Rings$Med_IM_DStrArea)]<-0
Teo_Rings$Avg_IM_DStrPop[is.nan(Teo_Rings$Avg_IM_DStrPop)]<-0
Teo_Rings$Avg_Low_DStrArea[is.nan(Teo_Rings$Avg_Low_DStrArea)]<-0
Teo_Rings$Med_Low_DStrArea[is.nan(Teo_Rings$Med_Low_DStrArea)]<-0
Teo_Rings$Avg_UncerStat_DStrArea[is.nan(Teo_Rings$Avg_UncerStat_DStrArea)]<-0
Teo_Rings$Med_UncerStat_DStrArea[is.nan(Teo_Rings$Med_UncerStat_DStrArea)]<-0
Teo_Rings$Avg_UncerStat_DStrPop[is.nan(Teo_Rings$Avg_UncerStat_DStrPop)]<-0    
Teo_Rings[is.na(Teo_Rings)] <- 0
```

 [1] "Ring"                   "Pop_TOT"                "DStr_TOT"               "Area_DStr"             
 [5] "NonCC_Feat_TOT"         "NonCC_Feat_Area"        "NonCCDStr_TOT"          "NonCCDStr_Area"        
 [9] "OB"                     "OB_Area"                "Unoccu"                 "Unoccu_Area"           
[13] "DomPlat"                "DomPlat_Area"           "Unk"                    "Unk_Area"              
[17] "CCStr"                  "CCStrArea"              "AoD"                    "AoD_Area"              
[21] "Plazas"                 "Plaza_Area"             "PlazAoD_O"              "PlazAoD_O_Area"        
[25] "CCFeat_AoD_Area"        "CCFeat_O_Area"          "UnOccuFeat"             "UnOccuFeat_Area"       
[29] "Elite_DStr"             "Elite_Pop"              "Elite_DStrArea"         "Avg_Elite_DStrArea"    
[33] "Med_Elite_DStrArea"     "Avg_Elite_DStrPop"      "IM_DStr"                "IM_Pop"                
[37] "IM_DStrArea"            "Avg_IM_DStrArea"        "Med_IM_DStrArea"        "Avg_IM_DStrPop"        
[41] "Low_DStr"               "Low_Pop"                "Low_DStrArea"           "Avg_Low_DStrArea"      
[45] "Med_Low_DStrArea"       "Avg_Low_DStrPop"        "UncerStat_DStr"         "UncerStat_Pop"         
[49] "UncerStat_Area"         "Avg_UncerStat_DStrArea" "Med_UncerStat_DStrArea" "Avg_UncerStat_DStrPop" 



## Construct Ring Dataset

```{r label='', message=FALSE,warning=FALSE}

Ring <- c(1:nrings)    
MinRingDist <- seq(0,((nrings-1)*500),by=500)
MedRingDist <- seq(250,(((nrings-1)*500)+250),by=500)
MaxRingDist <- seq(500,(((nrings-1)*500)+500),by=500)
Ring_Area <- RingsPoly@data$Area_ha
Popdens_TOT = Teo_Rings$Pop_TOT / Ring_Area
Pop_TOT = Teo_Rings$Pop_TOT
DStr_TOT = Teo_Rings$DStr_TOT
Area_DStr = Teo_Rings$Area_DStr
Ring_Data <- data.frame(Ring,MinRingDist,MedRingDist,MaxRingDist,Ring_Area,Pop_TOT,Popdens_TOT,DStr_TOT,Area_DStr)
Next <- Teo_Rings[,c(5:28)]
Elite <- Teo_Rings[,c(29:34)]
IM <- Teo_Rings[,c(35:40)]
Low <- Teo_Rings[,c(41:46)]
UncertStat <- Teo_Rings[,c(47:52)]

Ring_Data <-cbind(Ring_Data, Next)


Ring_Data <- Ring_Data %>%
    mutate(Popdens_DStrArea = Pop_TOT / Area_DStr,
    Area_NonDStr = Ring_Area - Area_DStr,
    Area_NonCCZone = Ring_Area - CCStrArea,
    Popdens_NonCCZone = Pop_TOT / Area_NonCCZone,
    Area_NonCCZone_AoD = Ring_Area - CCFeat_AoD_Area,
    Popdens_NonCCZone_AoD = Pop_TOT / Area_NonCCZone_AoD,
    Area_NonCCZone_O = Ring_Area - CCFeat_O_Area,
    Popdens_NonCCZone_O = Pop_TOT / Area_NonCCZone_O,
    Area_Open = Ring_Area - (NonCC_Feat_Area + CCFeat_O_Area),
    Area_OpenUnoccu = Ring_Area - ((NonCC_Feat_Area - Unoccu_Area) + CCFeat_O_Area),
    PctRow_Area_DStr = Area_DStr / Ring_Area,
    PctRow_Area_NonDStr = (Ring_Area - Area_DStr) / Ring_Area,
    PctRow_Area_CCFeat_AoD = CCFeat_AoD_Area / Ring_Area,
    PctRow_Area_CCFeat_O = CCFeat_O_Area / Ring_Area,
    PctRow_Area_CCStr = CCStrArea / Ring_Area,
    PctRow_Area_Open = Area_Open / Ring_Area,
    PctRow_Area_OpenUnoccu = Area_OpenUnoccu / Ring_Area,
    PctRow_Area_NonCCZone = Area_NonCCZone / Ring_Area,
    PctRow_Area_NonCCZone_AoD = Area_NonCCZone_AoD / Ring_Area,
    PctRow_Area_NonCCZone_O = Area_NonCCZone_O / Ring_Area,
    PctRow_Area_UnOccuFeat = UnOccuFeat_Area / Ring_Area,
    PctRow_Area_Unk = Unk_Area / Ring_Area,
    PctRow_Area_OB = OB_Area / Ring_Area,
    PctRow_Area_AoD = AoD_Area / Ring_Area,
    PctRow_Area_Plazas = Plaza_Area / Ring_Area,
    PctRow_Area_DomPlat = DomPlat_Area / Ring_Area,
    PctCol_Area_DStr = Area_DStr / sum(Area_DStr),
    PctCol_Area_NonDStr = Area_NonDStr / sum(Area_NonDStr),

    PctCol_Area_CCFeat_AoD = CCFeat_AoD_Area / sum(CCFeat_AoD_Area),
    PctCol_Area_CCFeat_O = CCFeat_O_Area / sum(CCFeat_O_Area),

    PctCol_Area_CCStr = CCStrArea / sum(CCStrArea),
    PctCol_Area_Open = Area_Open / sum(Area_Open),
    PctCol_Area_OpenFields = Area_OpenUnoccu / sum(Area_OpenUnoccu),
    PctCol_Area_NonCCZone = Area_NonCCZone / sum(Area_NonCCZone),
    PctCol_Area_NonCCZone_M = Area_NonCCZone_AoD / sum(Area_NonCCZone_AoD),
    PctCol_Area_NonCCZone_O = Area_NonCCZone_O / sum(Area_NonCCZone_O),
    PctCol_Area_UnOccuFeat = UnOccuFeat_Area / sum(UnOccuFeat_Area),
    PctCol_Area_Unk = Unk_Area / sum(Unk_Area),
    PctCol_Area_OB = OB_Area / sum(OB_Area),
    PctCol_Area_AoD = AoD_Area / sum(AoD_Area),
    PctCol_Area_Plazas = Plaza_Area / sum(Plaza_Area),
    PctCol_Area_DomPlat = DomPlat_Area / sum(DomPlat_Area))
    
Ring_Data <-cbind(Ring_Data, Elite)

Ring_Data <- Ring_Data %>%
    mutate(PctRow_DStr_Elite = Elite_DStr / DStr_TOT,
    PctRow_Pop_Elite = Elite_Pop / Pop_TOT,
    PctRow_DStrArea_Elite = Elite_DStrArea / Area_DStr,
    PctCol_DStr_Elite = Elite_DStr / sum(Elite_DStr),
    PctCol_Pop_Elite = Elite_Pop / sum(Elite_Pop),
    PctCol_DStrArea_Elite = Elite_DStrArea / sum(Elite_DStrArea),
    Elite_Popdens_NonCCZone = Elite_Pop / Area_NonCCZone,
    Elite_Popdens_NonCCZone_AoD = Elite_Pop / Area_NonCCZone_AoD,
    Elite_Popdens_NonCCZone_O = Elite_Pop / Area_NonCCZone_O,
    Elite_Popdens_EliteDStrArea = Elite_Pop / Elite_DStrArea,
    Elite_Popdens_TOTArea = Elite_Pop / Ring_Area)

Ring_Data$PctCol_DStrArea_Elite[is.nan(Ring_Data$PctCol_DStrArea_Elite)]<-0
Ring_Data$Elite_Popdens_EliteDStrArea[is.nan(Ring_Data$Elite_Popdens_EliteDStrArea)]<-0


Ring_Data <-cbind(Ring_Data, IM)
Ring_Data <- Ring_Data %>%
    mutate(PctRow_DStr_IM = IM_DStr / DStr_TOT,
    PctRow_Pop_IM = IM_Pop / Pop_TOT,
    PctRow_DStrArea_IM = IM_DStrArea / Area_DStr,
    PctCol_DStr_IM = IM_DStr / sum(IM_DStr),
    PctCol_Pop_IM = IM_Pop / sum(IM_Pop),
    PctCol_DStrArea_IM = IM_DStrArea / sum(IM_DStrArea),
    IM_Popdens_NonCCZone = IM_Pop / Area_NonCCZone,
    IM_Popdens_NonCCZone_AoD = IM_Pop / Area_NonCCZone_AoD,
    IM_Popdens_NonCCZone_O = IM_Pop / Area_NonCCZone_O,
    IM_Popdens_IMDStrArea = IM_Pop / IM_DStrArea,
    IM_Popdens_TOTArea = IM_Pop / Ring_Area)
    


Ring_Data <-cbind(Ring_Data, Low)
    
Ring_Data <- Ring_Data %>%
    mutate(PctRow_Ring_DStr_Low = Low_DStr / DStr_TOT,
    PctRow_Ring_Pop_Low = Low_Pop / Pop_TOT,
    PctRow_Ring_DStrArea_Low = Low_DStrArea / Area_DStr,
    PctCol_Tot_LowDStr = Low_DStr / sum(Low_DStr),
    PctCol_Tot_LowPop = Low_Pop / sum(Low_Pop),
    PctCol_Tot_LowDStrArea = Low_DStrArea / sum(Low_DStrArea),
    Low_Popdens_NonCCZone = Low_Pop / Area_NonCCZone,
    Low_Popdens_NonCCZone_AoD = Low_Pop / Area_NonCCZone_AoD,
    Low_Popdens_NonCCZone_O = Low_Pop / Area_NonCCZone_O,
    Low_Popdens_TOTArea = Low_Pop / Ring_Area,
    Low_Popdens_OpenArea = Low_Pop / Area_Open,
    Low_Popdens_LowDStrArea = Low_Pop / Low_DStrArea)
    

Ring_Data <-cbind(Ring_Data, UncertStat)
    
Ring_Data <- Ring_Data %>%
    mutate(PctRow_DStr_UncerStat = UncerStat_DStr / DStr_TOT,
    PctRow_Pop_UncerStat = UncerStat_Pop / Pop_TOT,
    PctRow_DStrArea_UncerStat = UncerStat_Area / Area_DStr,
    PctCol_DStr_UncerStat = UncerStat_DStr / sum(UncerStat_DStr),
    PctCol_Pop_UncerStat = UncerStat_Pop / sum(UncerStat_Pop),
    PctCol_DStrArea_UncerStat = UncerStat_Area / sum(UncerStat_Area),
    UncerStat_Popdens_NonCCZone = UncerStat_Pop / Area_NonCCZone,
    UncerStat_Popdens_NonCCZone_AoD = UncerStat_Pop / Area_NonCCZone_AoD,
    UncerStat_Popdens_NonCCZone_O = UncerStat_Pop / Area_NonCCZone_O,
    UncerStat_Popdens_TOTArea = UncerStat_Pop / Ring_Area,
    UncetStat_Popdens_OpenArea = UncerStat_Pop / Area_Open,
    UncerStat_Popdens_UncerStatDStrArea = UncerStat_Pop / UncerStat_Area)
    

```







## Ring Dataset Variables











# Export Datasets for Analysis

```{r}

write.csv(TeoRings_Circ, paste0(wd$data_f,"TeoRings_Circ.csv"))

write.csv(TeoRings_Oval, paste0(wd$data_f,"TeoRings_Oval.csv"))

writeOGR(Teo_ArchPoly_Data, paste0(wd$data_f,"Teo_ArchPoly_Data.gpkg"), "Teo_ArchPoly_Data", driver = "GPKG", overwrite_layer=TRUE)

```





yy = TeoArch_Pts %>% filter(is.na(Ring_Circle))
>   Teo_Poly_Data <- sp::merge(TeoArch_Poly, TeoArch_Pts, by="ID")
> xx = Teo_Poly_Data@data %>% filter(is.na(Ring_Circle))




